### 2021-01-04 abstract.tex
Initial Overleaf Import

\documentclass[a4paper,10pt]{article}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
columnsep=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{boxedminipage}
\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[font=it]{caption}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
%\renewcommand{\baselinestretch}{0.7}
% FOR enumerates
\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
\setenumerate{leftmargin=*}
\setcounter{secnumdepth}{-1}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%																 END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{-1.5cm} at the top
\title{Simulation and visualisation of mitigation and adaption strategy pathways for urban districts}																																		% Line 2 
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{
Justin McCarty, Adam Rysanek

\phantom{Line 9}} 																								
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line
%																 END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\section{Aims and Approaches} 
At present mitigation and adaptations strategies compete for constrained resources within a future of uncertain climate impacts. Meeting decarbonisation goals while implementing robust and resilient adaptions strategies requires an analysis structure that can account for uncertainty as well as depict how the intermingling of strategies may hinder or benefit the ultimate trajectory of actions. A recently constructed community of 15,000 in Vancouver, BC (Wesbrook Village) offers a case study in how to recommend decarbonisation and adaptation planning decisions through near-exhaustive building simulation. In this paper the model of this growing urban district is described, following Fonseca et al.'s method (2016), several mitigation and adaptation strategies are simulated under climate change uncertainty, following Nik (2017), for their independent and compounding effects on total carbon emissions and total economic cost, and a visualization and decisions analysis strategy is described that can help planners in constructing pathways under a range of climate change and development pathways.

% Previous research on this community has shown that a planned neighbourhood energy systems is not able to compete on a carbon performance level as the regional electricity grid depending on whether operating carbon and/or embodied carbon is assessed. The same issue is foreseen on decision around construction material and community density. This paper incorporates elements of life-cycle emissions accounting in a previously-published sequential search-based building simulation process. The work assesses the Wesbrook Village site to determine, from the perspective of the municipality, the least-cost carbon reduction pathway that includes both operating and embodied emissions - and yet still achieves the community’s growth targets.

\section{Scientific Innovation and Relevance}
The marginal abatement cost (MAC) curve is an indispensable tool for planning mitigation pathways, but has historically not relied upon robust experimental analysis making it notional at best. The contribution of this research follows on the critique of simplistic MAC curves by Kesicki et al. (2011) and the evolution of MAC curve methodology in Ryansek et al. (2013), building into the curve a view of adaptation cost and the residual cost of climate change. This inclusion allows planners to more holistically evaluate the benefit of mitigation strategies in the context of direct climate impact. Additionally this study evaluates the embodied carbon associated with built environment decision making. Visualizing and discussing the sensitivity of simulation-based building design decisions to questions of operating vs. embodied carbon are important. It is not yet established whether factoring embodied carbon (and/or energy) is necessary for robust simulation-based decision-making on low-carbon building and energy systems.

% This work will result in the production of marginal carbon abatement cost curves for an urban community that include both operating and embodied carbon, as well as the effect of individual technologies on real estate value and revenue, and display the  This is the first known simulation study to do so, and so this work seeks to contribute to best practise building performance simulation assessment in the coming century. The work makes use of future climate weather files under varying climate scenarios, to forecast long-term trends in building performance and comfort. Likewise, variable future cost scenarios are considered in a discounted cash flow analysis. Embodied carbon is also accounted for in the simulation process, such that every design intervention, whether it be a building technology change (i.e., upgrade of double glazing to triple glazing) or a future energy system choice is attributed with a projected value of operating carbon emissions, embodied carbon emissions, and real estate value and revenue.

\section{Preliminary Results and Conclusions}
Our initial results indicate that inclusion of embodied carbon into simulation analysis alters cost-optimal community design decision in a number of manners. For Wesbrook Village in Vancouver, BC, we see that when considering embodied carbon, the favourability of electrifying heating systems of existing buildings in a simple manner (i.e., using baseboard electric heaters) becomes preferred over upgrading existing natural gas central heating systems to electric heat pumps. Most importantly, the results indicate the importance of retaining and expanding a typology of mid-rise residential buildings, which are based on timber-frame construction and yield a significantly lower carbon footprint than any development scenario that encourages construction of high-rise, concrete buildings.
\section{Main References}

\begin{enumerate}
    \item Fonseca, J. A., Nguyen, T.-A., Schlueter, A., & Marechal, F. (2016). City Energy Analyst (CEA): Integrated framework for analysis and optimization of building energy systems in neighborhoods and city districts. Energy and Buildings, 113, 202–226. https://doi.org/10.1016/j.enbuild.2015.11.055
    \item Nik, V. M. (2017). Application of typical and extreme weather data sets in the hygrothermal simulation of building components for future climate – A case study for a wooden frame wall. Energy and Buildings, 154, 30–45. https://doi.org/10.1016/j.enbuild.2017.08.042
    \item Kesicki, F and Strachan, N (2011). Marginal abatement cost (MAC) curves: confronting theory and practice. Environmental Science \& Policy, 14-8, 1195-1204.
    \item Rysanek, A. M., & Choudhary, R. (2013). Using building simulation to create marginal abatement cost curves of individual buildings. 13th Conference of International Building Performance Simulation, 1877-1884.
\end{enumerate}

\end{document}

### 2021-01-04 format guide.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template revision history:
% BS2021: Revised by Filip Jorissen, filip.jorissen@kuleuven.be
% BS2019: Revised by Alessandro Prada, alessandro.prada@unitn.it
% BS2017: Initial version by Michael Wetter, mwetter@lbl.gov
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[twocolumn, a4paper,10pt]{article}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
columnsep=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{boxedminipage}
\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[font=it]{caption}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
%\renewcommand{\baselinestretch}{0.7}
% FOR enumerates
\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
\setenumerate{leftmargin=*}
\setcounter{secnumdepth}{-1}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Paper Preparation Guide and Submission Instructions for\\																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
\vspace{4pt}
Building Simulation 2021 Conference} 																																% Line 2 
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
Jane Doe$^1$, Richard Roe$^2$, John Stiles$^2$\\ 																										% Line 4
$^1$Institution 1, City 1, Country 1\\ 																																	% Line 5
$^2$Institution 2, City 2, Country 2\\ 																																	% Line 6
% comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
\textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}\\ 			 			  	% Line 7
\textit{(leave blank up to line 10 - remove line numbering from final version)}\\ 															% Line 8
\phantom{Line 9}} 																																									% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														% Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

\section*{Abstract}	% Section headings need to be upper and lower case.
\addtocounter{section}{1}
This document explains how to prepare a paper for submission to the Building Simulation 2021 Conference. It also includes the instructions for submission and some other information. This file can also be used as a template if you are using MS-Word. In this case you can use the preselected styles in the Style Gallery to format the document.

\section*{Key Innovations}
\begin{itemize}
\item Key innovations section added
\item Practical implications section added
\end{itemize}

\section*{Practical Implications}
This updated template allows practitioners to quickly grasp the practical implications of any paper. Use it and share your work to a broader audience!

\section*{Introduction}
The paper should be prepared in A4 size, portrait oriented, with 25 mm margins at top and bottom, and 20 mm margins at left and right. Use font type Times (Times New Roman) for the entire document with different style at different part of the paper, as explained later. The \textbf{maximum number of pages is 8}. Please \textbf{\underline{do not}} add page numbers, headers or footers.\\
The paper includes 2 sections (top section and main body) and different parts. Mandatory - in bold - and optional (recommended but not limited to) parts are:\\
Top section
\begin{itemize}
\item \textbf{Title}
\item \textbf{Authors}
\item \textbf{Authors' affiliations}
\end{itemize}
Main body
\begin{itemize}
\item \textbf{Abstract}
\item \textbf{Key innovations}
\item \textbf{Practical implications}
\item \textbf{Introduction}
\item Methods
\item Results
\item Discussion
\item \textbf{Conclusion}
\item Acknowledgments
\item Nomenclature
\item \textbf{References}
\end{itemize}
Optional parts can be replaced according to the needs but the order should be preserved.\\
Second level paragraphs are acceptable. Lower level paragraphs are discouraged.\\
Do not leave empty lines between titles, paragraphs and figures in the main body. Use paragraph spacing above and below titles and paragraphs as specified in the following. \\
In case you use MS-Word, you can refer to the predefined styles in the gallery included in the MS-word template (in alphabetical order):
\begin{itemize}
\item Authors
\item Captions
\item Equation
\item Figure
\item List (bulleted)
\item List (numbered)
\item Heading 1
\item Heading 2
\item Normal
\item Reference
\item Tables
\item Title
\end{itemize}
%---------------------------------------------------------------------------------------
\section*{Parts of the paper: top section}
%---------------------------------------------------------------------------------------
The top section of the first page of the paper is used for the title of the paper, list of authors, and authors' affiliation. This section always consists of 10 lines of exactly 14 points spacing, in single column format.
\subsection*{Title, authors, and authors' affiliations}
Titles (MS-word: select \textit{Title style}) should be in bold font size 12 points. Do not use more than 2 lines for the title, and try to limit it to ten words.\\
Authors (MS-word: select \textit{Authors style}), authors' affiliations, and other information should be in font size 12 points. In case of more than one affiliation, reference superscripts after the author's names and before the corresponding affiliation will be added.\\
Authors' affiliations (MS-word: \textit{always in Authors style}), can include contact (e-mails, telephone numbers, postal address, etc.) and other information. However, the 10 lines limitation applies. If you need less than 10 lines for all the information, please leave the remaining lines blank.
%---------------------------------------------------------------------------------------
\section*{Main body}
%---------------------------------------------------------------------------------------
After the 10 lines in the top section, the rest of the document is in two-column format, with a space between the two columns of 80 mm. The space between the columns should be centred on the paper. Line spacing is exactly 12 points.\\
The main text should be typed in 10 point font, justified, with 3 points spacing below each paragraph (\textit{MS-word: select \textit{Normal style}}).\\
The headings of each section should use font size of 12 point, capitalized, with 3 and 3 points spacing above and below (\textit{MS-word: select \textit{Heading 1 style}}). The headings of the subsection should use 10 points size and bold, with 3 points spacing below (\textit{MS-word: select \textit{Heading 2 style}}). Left alignment is used for headings. Both the sections and subsections \underline{\textbf{should not}} be numbered.
%---------------------------------------------------------------------------------------
\subsection*{Abstract}
%---------------------------------------------------------------------------------------
The abstract of your paper should be about 100 words.\\
Abstracts must clearly identify (i) what is the current state of the art, (ii) what are its deficiencies, (iii) what methods have been applied, (iv) what are the results, and (v) what is the lasting contribution of the submission.
%---------------------------------------------------------------------------------------
\subsection*{Key inovations}
%---------------------------------------------------------------------------------------
In 1-5 bullet points, clearly highlight where this paper moves beyond the state of the art.
%---------------------------------------------------------------------------------------
\subsection*{Practical implications}
%---------------------------------------------------------------------------------------
The practical implications section should be about 20 - 50 words.\\
Capture succinctly what a simulation practitioner should take away from your paper: always do \ldots ; avoid  \ldots; consider x and beware of y in case of  \ldots

%---------------------------------------------------------------------------------------
\subsection*{Figures and Tables}
%---------------------------------------------------------------------------------------
Figures and Tables are preferably included in the text where they are discussed rather than at the end of the paper. In the case of figures, select the ``In line with text" from the layout options if you use MS-Word. A centred alignment with 3 and 3 points spacing above and below is required (\textit{MS-word: select \textit{Figure style}}). \\
Both figures and tables must have a number and caption. Figure~\ref{fig:fig01} (\textit{refer this way to a figure in the text, do not use Fig. ~\ref{fig:fig01} or figure ~\ref{fig:fig01}}) is an example of a graph in the text. Captions (\textit{MS-word: use \textit{Captions style}}) always follow the figure in italic font size 10 points, and centred, with 3 and 3 points spacing above and below.\\
If figures authorship does not belong to one of the authors, authors are required to ask to the copyright owner the permission to use that material and to provide a proof that the permission has been accorded.\\
Colour images are welcome.\\
\begin{figure}
\centering
\includegraphics[scale=1.0]{img/fig1.pdf}
\caption{A gentle reminder.}
\label{fig:fig01}
\vspace{-16pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{figure}
Table \ref{tab:tab01} shows an example of a table, where the caption should be on the top of the table, with the same format as figure captions. Text in tables can be in font size of 9 points and centred, with no spacing above and below (MS-word: use \textit{Tables style}).
\begin{table}[ht]
\vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\caption{Example of a table.}
\label{tab:tab01}
\centering
\begin{tabular}{| c | c | c | }
  \hline
  \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
  \hline
  Entry 1 & Entry 2 & Entry 3 \\
  \hline
\end{tabular}
\vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table}
Oversized figures and tables may be included in the text. However, authors may arrange the layout properly so that it appears at the top or the bottom of the page, or preferably on a separate page at the end of the paper. Figure ~\ref{fig:fig02} is an example of an oversized figure.
%---------------------------------------------------------------------------------------
\subsection*{Equations and units}
%---------------------------------------------------------------------------------------
Each significant equation or formula should be displayed on a separate line. Center equations and place consecutive equation numbers flush right in parentheses. For example,
\begin{equation}\label{eq:example}
  a^2+b^2=c^2.
\end{equation}
If you use MS-Word, use the Equation style and use tabs to position equations and equation numbers correctly.
Mathematical symbols should be clear and avoid ambiguities. Keep using font size 10 points. Symbols representing physical quantities (or variables) are italic. Symbols representing units, operators, labels and numbers, are regular (upright).\\
Equations should be referenced in the text by their number (\ref{eq:example}). A brief description of the symbols used in your paper should be added in a nomenclature section at the end of the text or inline with the text where the symbols are first used.\\
SI units of measurement are mandatory. If other units are mentioned, always provide their equivalent value according to SI.\\
SI notation must be adopted as regards symbols, prefixes and other writing rules. In particular comma as a decimal separator is preferred to the point (which is anyhow allowed if used consistently throughout the manuscript). If needed, only blank spaces are allowed as thousand separators.
%---------------------------------------------------------------------------------------
\subsection*{References}
%---------------------------------------------------------------------------------------
All publications cited in the text should be listed at the end of the Main body in a References section, in alphabetical order of the family name of the first author. From the second line on, each entry should be indented by 5 mm. Justified alignment with 3 and 3 points spacing above and below each paragraph must be used (\textit{MS-word: select \textit{Reference style}}). Examples of reference style are reported in the reference section below for journals, conference proceedings, books and technical standards.\\
In the main text, refer to a reference using author-year style such as \citet{Clarke2015:1} or \citet{ChuMajumdar2012}. When the reference is not a part of the sentence, use the author-year style in brackets (\cite{Clarke2015:1, ChuMajumdar2012,Monarim2014, BSDO2011, Mahdavi2011,iso52017}).
%---------------------------------------------------------------------------------------
\subsection*{Bulleted and numbered lists}
%---------------------------------------------------------------------------------------
Numbered and bulleted lists must be justified, with no indentation, and 5 mm hanging. You may use List (bulleted) or List (Numbered) styles in MS-Word.
%---------------------------------------------------------------------------------------
\section*{If you use MS-Word}
%---------------------------------------------------------------------------------------
You can use the .docx document as a template if you use MS-Word. Please use the style for each section as has been defined in the template. You can either use the template, rename it, and cut-and-paste your paper from other document(s) into the template, or you can use your document, open style organizer (Format – Style and then click ``organizer"), delete all your styles and import the styles from the template.
If you use the template, do not forget to disable the line number on the Top section of the first page before you submit the paper and cancel instructions comments (\textit{in brackets and italic fonts}).
%---------------------------------------------------------------------------------------
\section*{If you use \LaTeX}
%---------------------------------------------------------------------------------------
Please use the \LaTeX template you can download from the conference website. In the compressed folder, you will find:
\begin{itemize}
\item \textbf{format guide.tex}: a fill-in form for a standard article with usage comments. Please copy it to a new file with a new name and use it as the basis for your article.
\item \textbf{reference.bib}: is a plain text containing the database of the references used for the format guide. Please use the same entries included in this file for your database.
\item \textbf{BS2021.bst}: is the bibliography style of the conference proceedings. 
\end{itemize}
%---------------------------------------------------------------------------------------
\section*{Submission instruction}
%---------------------------------------------------------------------------------------
\begin{enumerate}
    \item To enable the blind review process please do not include your name and affiliation on the draft submitted for review. This information will be requested in the final submission.
    \item Please convert your entire document to PDF format. An additional doc/\LaTeX version of the manuscript can be optionally added. In this case a single .zip file including both the .pdf and the doc/\LaTeX files of your contribution shall be uploaded.
    \item Papers must be at most 8 pages long.
    \item You can use any file name, but please do not use special characters, umlaute, etc.
    \item The maximum file size is 10 MB, but please use vector graphics where possible to reduce your file size.
		\item If your paper has not met all the requirements for submission, your file \textbf{will not be processed for review and you will be requested to resubmit}. If everything is in order, the paper will be up-loaded to the review area of the conference web site.
\end{enumerate}
%---------------------------------------------------------------------------------------
\section*{Conclusion}
%---------------------------------------------------------------------------------------
This paper has shown how to prepare a paper for submission to Building Simulation 2021 Conference. Good luck with your paper. 
%---------------------------------------------------------------------------------------
\section*{Acknowledgment}
%---------------------------------------------------------------------------------------
This document is a summary of various documents from previous Building Simulation Conferences.
%here starts the references
\bibliographystyle{BS2021}
\bibliography{references}
\newpage
\onecolumn
Please \textbf{do not} include this disclaimer in your paper.  You will be required to accept these conditions when you  submit your paper via the web site.

\begin{figure*}[ht]
\centering
\begin{boxedminipage}{\textwidth}
Building Simulation 2021\\

I or we, the author(s) and presenter(s) of the conference contribution ``Automatic generation of second level space boundary geometry from IFC models'', have read the following Copyright Transfer and Disclaimer, and agree to them by submitting the final contribution materials.

 \begin{enumerate}
 \item The author(s) and presenter(s) will automatically grant to IBPSA a nonexclusive, royalty-free, perpetual, worldwide, irrevocable, sub-licensable, and transferable license to publish the abstract(s), research paper(s) and/or presentation(s) and/or digital posters (with unmodified content) in any fashion (including but not limited to inclusion in the Building Simulation 2021 printed and electronic proceedings, via electronic means such as the world wide web, and inclusion in future compilations of presentations, also including online-exploitation via electronic means in order to organize an e-conference, regardless of the accessibility through paying registration). This ``nonexclusive'' license means that the author(s) are not restricted as to future use of the material except that exclusive rights cannot be granted to another.

\item The author(s) and presenter(s) grant and assign to IBPSA or its agent the nonexclusive rights to record the presentation at the Building Simulation 2021 conference in Bruges, Belgium. These rights give IBPSA the unlimited license to use, modify (format, not content), sell and distribute the recorded presentation (including voice of the presenter(s)).

\item The author(s) and presenter(s) affirm that they have the right to grant the license specified in (1) and (2), that is, publication by IBPSA or its licensees will not be in conflict with existing copyright or other restrictions.

\item The author(s) and presenter(s) acknowledge that acceptance of the abstract(s), research paper(s) and/or presentation(s) does not imply IBPSA's endorsement of or agreement with the ideas presented. It is understood that IBPSA does not accept responsibility for any content within the abstract(s), research paper(s) and/or presentation(s) that may be found to be libelous, infringing on copyright or other intellectual property rights, invading individual privacy or to be otherwise unlawful. Under no circumstances shall IBPSA be liable for any damages resulting from use of information included in the presentation.

\item Finally, the undersigned confirms that he/she has the power and authority to make and execute this agreement. For jointly authored works the signing author/presenter signs as authorized agent for the others.
 \end{enumerate}

\end{boxedminipage}
\caption{The author will be required to accept these conditions when they submit their paper via the web site.}
\label{fig:fig02}
\end{figure*}

\end{document}

### 2021-01-04 manuscript_wesbrook-bigmacc_BS2021.tex
Initial Overleaf Import

--- 2021-01-04 format guide.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+% Simulation and visualisation of mitigation and adaption strategy pathways for urban districts
 %%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \title{%
-Paper Preparation Guide and Submission Instructions for\\																								% Line 1
+Visualizing climate change mitigation and adaptation pathways\\																								% Line 1
 %%% Please keep the \vspace{4pt} between lines in the title
 \vspace{4pt}
-Building Simulation 2021 Conference} 																																% Line 2 
+for new urban development} 																																% Line 2 
 %If there is no second line then just put \phantom{Line 2} here
@@
 \author{																																														% Line 3
-Jane Doe$^1$, Richard Roe$^2$, John Stiles$^2$\\ 																										% Line 4
-$^1$Institution 1, City 1, Country 1\\ 																																	% Line 5
-$^2$Institution 2, City 2, Country 2\\ 																																	% Line 6
+% Justin McCarty$^1$, Adam Rysanek$^1$
+\\ 																				% Line 4
+% $^1$The University of British Columbia, Vancouver, Canada
+\\ 																																                                                            	% Line 5
+% $^2$Institution 2, City 2, Country 2
+\\ 																																                                                                % Line 6
 % comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
-\textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}\\ 			 			  	% Line 7
-\textit{(leave blank up to line 10 - remove line numbering from final version)}\\ 															% Line 8
+% \textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}
+\\ 			 			  	                                                    % Line 7
+% \textit{(leave blank up to line 10 - remove line numbering from final version)}
+\\ 														                    	% Line 8
 \phantom{Line 9}} 																																								            	% Line 9
@@
 \addtocounter{section}{1}
-This document explains how to prepare a paper for submission to the Building Simulation 2021 Conference.
-It also includes the instructions for submission and some other information.
-This file can also be used as a template if you are using MS-Word.
-In this case you can use the preselected styles in the Style Gallery to format the document.
+At present mitigation and adaptations strategies compete for constrained resources within a future of uncertain climate impacts.
+Meeting decarbonisation goals while implementing robust and resilient adaptions strategies requires an analysis structure that can account for uncertainty as well as depict how the intermingling of strategies may hinder or benefit the ultimate trajectory of actions.
+The marginal abatement cost curve (MACC) is an indispensable tool for planning mitigation pathways, but has historically not relied upon robust experimental analysis making it notional at best nor has it included a view of adaptation pathways.
+This study utilizes a recently developed and nearly finished medium-density community in Vancouver, British Columbia, Canada of 15,000 residents as a case study for developing a pathway based MACC.
+Multiple mitigation and adaptation measures are modeled individually and through exhaustive combination to test their sensitivity on marginal abatement cost and residual cost of climate change.
+The resulting MACCs are compared with more tradition decision support visualizations to argue for a more comprehensive approach to decarbonisation and adaptation planning.
 
@@
 \begin{itemize}
-\item Key innovations section added
-\item Practical implications section added
+\item Intermingling of mitigation and adaptation strategies in a MACC.
+\item 
 \end{itemize}
@@
 \section*{Practical Implications}
-This updated template allows practitioners to quickly grasp the practical implications of any paper. Use it and share your work to a broader audience!
-
-\section*{Introduction}
-The paper should be prepared in A4 size, portrait oriented, with 25 mm margins at top and bottom, and 20 mm margins at left and right.
-Use font type Times (Times New Roman) for the entire document with different style at different part of the paper, as explained later.
-The \textbf{maximum number of pages is 8}.
-Please \textbf{\underline{do not}} add page numbers, headers or footers.\\
-The paper includes 2 sections (top section and main body) and different parts. Mandatory - in bold - and optional (recommended but not limited to) parts are:\\
-Top section
-\begin{itemize}
-\item \textbf{Title}
-\item \textbf{Authors}
-\item \textbf{Authors' affiliations}
-\end{itemize}
-Main body
-\begin{itemize}
-\item \textbf{Abstract}
-\item \textbf{Key innovations}
-\item \textbf{Practical implications}
-\item \textbf{Introduction}
-\item Methods
-\item Results
-\item Discussion
-\item \textbf{Conclusion}
-\item Acknowledgments
-\item Nomenclature
-\item \textbf{References}
-\end{itemize}
-Optional parts can be replaced according to the needs but the order should be preserved.\\
-Second level paragraphs are acceptable. Lower level paragraphs are discouraged.\\
-Do not leave empty lines between titles, paragraphs and figures in the main body. Use paragraph spacing above and below titles and paragraphs as specified in the following. \\
-In case you use MS-Word, you can refer to the predefined styles in the gallery included in the MS-word template (in alphabetical order):
-\begin{itemize}
-\item Authors
-\item Captions
-\item Equation
-\item Figure
-\item List (bulleted)
-\item List (numbered)
-\item Heading 1
-\item Heading 2
-\item Normal
-\item Reference
-\item Tables
-\item Title
-\end{itemize}
-%---------------------------------------------------------------------------------------
-\section*{Parts of the paper: top section}
-%---------------------------------------------------------------------------------------
-The top section of the first page of the paper is used for the title of the paper, list of authors, and authors' affiliation.
-This section always consists of 10 lines of exactly 14 points spacing, in single column format.
-\subsection*{Title, authors, and authors' affiliations}
-Titles (MS-word: select \textit{Title style}) should be in bold font size 12 points. Do not use more than 2 lines for the title, and try to limit it to ten words.\\
-Authors (MS-word: select \textit{Authors style}), authors' affiliations, and other information should be in font size 12 points.
-In case of more than one affiliation, reference superscripts after the author's names and before the corresponding affiliation will be added.\\
-Authors' affiliations (MS-word: \textit{always in Authors style}), can include contact (e-mails, telephone numbers, postal address, etc.) and other information.
-However, the 10 lines limitation applies.
-If you need less than 10 lines for all the information, please leave the remaining lines blank.
-%---------------------------------------------------------------------------------------
-\section*{Main body}
-%---------------------------------------------------------------------------------------
-After the 10 lines in the top section, the rest of the document is in two-column format, with a space between the two columns of 80 mm.
-The space between the columns should be centred on the paper.
-Line spacing is exactly 12 points.\\
-The main text should be typed in 10 point font, justified, with 3 points spacing below each paragraph (\textit{MS-word: select \textit{Normal style}}).\\
-The headings of each section should use font size of 12 point, capitalized, with 3 and 3 points spacing above and below (\textit{MS-word: select \textit{Heading 1 style}}).
-The headings of the subsection should use 10 points size and bold, with 3 points spacing below (\textit{MS-word: select \textit{Heading 2 style}}).
-Left alignment is used for headings.
-Both the sections and subsections \underline{\textbf{should not}} be numbered.
-%---------------------------------------------------------------------------------------
-\subsection*{Abstract}
-%---------------------------------------------------------------------------------------
-The abstract of your paper should be about 100 words.\\
-Abstracts must clearly identify (i) what is the current state of the art, (ii) what are its deficiencies, (iii) what methods have been applied, (iv) what are the results, and (v) what is the lasting contribution of the submission.
-%---------------------------------------------------------------------------------------
-\subsection*{Key inovations}
-%---------------------------------------------------------------------------------------
-In 1-5 bullet points, clearly highlight where this paper moves beyond the state of the art.
-%---------------------------------------------------------------------------------------
-\subsection*{Practical implications}
-%---------------------------------------------------------------------------------------
-The practical implications section should be about 20 - 50 words.\\
-Capture succinctly what a simulation practitioner should take away from your paper: always do \ldots ; avoid  \ldots; consider x and beware of y in case of  \ldots
+Open-source simulation tools can be used to test the sensitivity of different decarbonisation and adaptation strategies for an urban area, alowwing planners better models to make planning decisions.
 
 %---------------------------------------------------------------------------------------
-\subsection*{Figures and Tables}
+\section*{Introduction}
+
+Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, with recent estimates from global satellite observations placing the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C [ncdc].
+Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems [X attribution science report for 2020].
+Implementing adaptation strategies within the built environment is necessary to increase social resilience and protect human life and prevent economic damage, perhaps even bolster both [X cobenefits of adaptation paper].
+Simultaneously, the mitigation of present emissions, the abatement of possible future emissions, and the sequestration of atmospheric carbon is necessary to curtail increasingly dangerous and catastrophic levels of warming.
+This process of carbon drawdown is very familiar within studies of the built environment with strategies posed for transportation, buildings, agriculture, forestry, and other landuses.
+MItigationa and adaptation strategies though are rarely, if ever simultaneously tested in building
+
+In the presence of limited resources and a range of objectives, the cost and benefit of each strategy needs to be measured under a multitude of scenarios and in combination with other measures.
+This study will test the performance of adaptation and mitigation strategies alongside several development pathways and climate change scenarios for multiple population centers within BC.
+Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
+
+Lastly, the outcomes of such studies need to be presented and interacted with well
+
+\subsection*{}
+
 %---------------------------------------------------------------------------------------
-Figures and Tables are preferably included in the text where they are discussed rather than at the end of the paper.
-In the case of figures, select the ``In line with text" from the layout options if you use MS-Word.
-A centred alignment with 3 and 3 points spacing above and below is required (\textit{MS-word: select \textit{Figure style}}).
-\\
-Both figures and tables must have a number and caption.
-Figure~\ref{fig:fig01} (\textit{refer this way to a figure in the text, do not use Fig.
-~\ref{fig:fig01} or figure ~\ref{fig:fig01}}) is an example of a graph in the text.
-Captions (\textit{MS-word: use \textit{Captions style}}) always follow the figure in italic font size 10 points, and centred, with 3 and 3 points spacing above and below.\\
-If figures authorship does not belong to one of the authors, authors are required to ask to the copyright owner the permission to use that material and to provide a proof that the permission has been accorded.\\
-Colour images are welcome.\\
-\begin{figure}
-\centering
-\includegraphics[scale=1.0]{img/fig1.pdf}
-\caption{A gentle reminder.}
-\label{fig:fig01}
-\vspace{-16pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-\end{figure}
-Table \ref{tab:tab01} shows an example of a table, where the caption should be on the top of the table, with the same format as figure captions.
-Text in tables can be in font size of 9 points and centred, with no spacing above and below (MS-word: use \textit{Tables style}).
-\begin{table}[ht]
-\vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-\caption{Example of a table.}
-\label{tab:tab01}
-\centering
-\begin{tabular}{| c | c | c | }
-  \hline
-  \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
-  \hline
-  Entry 1 & Entry 2 & Entry 3 \\
-  \hline
-\end{tabular}
-\vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-\end{table}
-Oversized figures and tables may be included in the text.
-However, authors may arrange the layout properly so that it appears at the top or the bottom of the page, or preferably on a separate page at the end of the paper.
-Figure ~\ref{fig:fig02} is an example of an oversized figure.
+\section*{Methods}
+
+\subsection*{}
+
 %---------------------------------------------------------------------------------------
-\subsection*{Equations and units}
+\section*{Results}
+
+\subsection*{}
+
 %---------------------------------------------------------------------------------------
-Each significant equation or formula should be displayed on a separate line. Center equations and place consecutive equation numbers flush right in parentheses. For example,
-\begin{equation}\label{eq:example}
-  a^2+b^2=c^2.
-\end{equation}
-If you use MS-Word, use the Equation style and use tabs to position equations and equation numbers correctly.
-Mathematical symbols should be clear and avoid ambiguities.
-Keep using font size 10 points.
-Symbols representing physical quantities (or variables) are italic.
-Symbols representing units, operators, labels and numbers, are regular (upright).\\
-Equations should be referenced in the text by their number (\ref{eq:example}).
-A brief description of the symbols used in your paper should be added in a nomenclature section at the end of the text or inline with the text where the symbols are first used.\\
-SI units of measurement are mandatory. If other units are mentioned, always provide their equivalent value according to SI.\\
-SI notation must be adopted as regards symbols, prefixes and other writing rules.
-In particular comma as a decimal separator is preferred to the point (which is anyhow allowed if used consistently throughout the manuscript).
-If needed, only blank spaces are allowed as thousand separators.
-%---------------------------------------------------------------------------------------
-\subsection*{References}
-%---------------------------------------------------------------------------------------
-All publications cited in the text should be listed at the end of the Main body in a References section, in alphabetical order of the family name of the first author.
-From the second line on, each entry should be indented by 5 mm.
-Justified alignment with 3 and 3 points spacing above and below each paragraph must be used (\textit{MS-word: select \textit{Reference style}}).
-Examples of reference style are reported in the reference section below for journals, conference proceedings, books and technical standards.\\
-In the main text, refer to a reference using author-year style such as \citet{Clarke2015:1} or \citet{ChuMajumdar2012}.
-When the reference is not a part of the sentence, use the author-year style in brackets (\cite{Clarke2015:1, ChuMajumdar2012,Monarim2014, BSDO2011, Mahdavi2011,iso52017}).
-%---------------------------------------------------------------------------------------
-\subsection*{Bulleted and numbered lists}
-%---------------------------------------------------------------------------------------
-Numbered and bulleted lists must be justified, with no indentation, and 5 mm hanging. You may use List (bulleted) or List (Numbered) styles in MS-Word.
-%---------------------------------------------------------------------------------------
-\section*{If you use MS-Word}
-%---------------------------------------------------------------------------------------
-You can use the .docx document as a template if you use MS-Word.
-Please use the style for each section as has been defined in the template.
-You can either use the template, rename it, and cut-and-paste your paper from other document(s) into the template, or you can use your document, open style organizer (Format – Style and then click ``organizer"), delete all your styles and import the styles from the template.
-If you use the template, do not forget to disable the line number on the Top section of the first page before you submit the paper and cancel instructions comments (\textit{in brackets and italic fonts}).
-%---------------------------------------------------------------------------------------
-\section*{If you use \LaTeX}
-%---------------------------------------------------------------------------------------
-Please use the \LaTeX template you can download from the conference website. In the compressed folder, you will find:
-\begin{itemize}
-\item \textbf{format guide.tex}: a fill-in form for a standard article with usage comments. Please copy it to a new file with a new name and use it as the basis for your article.
-\item \textbf{reference.bib}: is a plain text containing the database of the references used for the format guide. Please use the same entries included in this file for your database.
-\item \textbf{BS2021.bst}: is the bibliography style of the conference proceedings. 
-\end{itemize}
-%---------------------------------------------------------------------------------------
-\section*{Submission instruction}
-%---------------------------------------------------------------------------------------
-\begin{enumerate}
-    \item To enable the blind review process please do not include your name and affiliation on the draft submitted for review. This information will be requested in the final submission.
-    \item Please convert your entire document to PDF format.
-An additional doc/\LaTeX version of the manuscript can be optionally added.
-In this case a single .zip file including both the .pdf and the doc/\LaTeX files of your contribution shall be uploaded.
-    \item Papers must be at most 8 pages long.
-    \item You can use any file name, but please do not use special characters, umlaute, etc.
-    \item The maximum file size is 10 MB, but please use vector graphics where possible to reduce your file size.
-		\item If your paper has not met all the requirements for submission, your file \textbf{will not be processed for review and you will be requested to resubmit}.
-If everything is in order, the paper will be up-loaded to the review area of the conference web site.
-\end{enumerate}
+\section*{Discussion}
+
+\subsection*{}
+
 %---------------------------------------------------------------------------------------
 \section*{Conclusion}
-%---------------------------------------------------------------------------------------
-This paper has shown how to prepare a paper for submission to Building Simulation 2021 Conference. Good luck with your paper. 
+
 %---------------------------------------------------------------------------------------
 \section*{Acknowledgment}
+
 %---------------------------------------------------------------------------------------
@@
 \centering
-\begin{boxedminipage}{\textwidth}
-Building Simulation 2021\\
 
-I or we, the author(s) and presenter(s) of the conference contribution ``Automatic generation of second level space boundary geometry from IFC models'', have read the following Copyright Transfer and Disclaimer, and agree to them by submitting the final contribution materials.
-
- \begin{enumerate}
- \item The author(s) and presenter(s) will automatically grant to IBPSA a nonexclusive, royalty-free, perpetual, worldwide, irrevocable, sub-licensable, and transferable license to publish the abstract(s), research paper(s) and/or presentation(s) and/or digital posters (with unmodified content) in any fashion (including but not limited to inclusion in the Building Simulation 2021 printed and electronic proceedings, via electronic means such as the world wide web, and inclusion in future compilations of presentations, also including online-exploitation via electronic means in order to organize an e-conference, regardless of the accessibility through paying registration).
-This ``nonexclusive'' license means that the author(s) are not restricted as to future use of the material except that exclusive rights cannot be granted to another.
-
-\item The author(s) and presenter(s) grant and assign to IBPSA or its agent the nonexclusive rights to record the presentation at the Building Simulation 2021 conference in Bruges, Belgium.
-These rights give IBPSA the unlimited license to use, modify (format, not content), sell and distribute the recorded presentation (including voice of the presenter(s)).
-
-\item The author(s) and presenter(s) affirm that they have the right to grant the license specified in (1) and (2), that is, publication by IBPSA or its licensees will not be in conflict with existing copyright or other restrictions.
-
-\item The author(s) and presenter(s) acknowledge that acceptance of the abstract(s), research paper(s) and/or presentation(s) does not imply IBPSA's endorsement of or agreement with the ideas presented.
-It is understood that IBPSA does not accept responsibility for any content within the abstract(s), research paper(s) and/or presentation(s) that may be found to be libelous, infringing on copyright or other intellectual property rights, invading individual privacy or to be otherwise unlawful.
-Under no circumstances shall IBPSA be liable for any damages resulting from use of information included in the presentation.
-
-\item Finally, the undersigned confirms that he/she has the power and authority to make and execute this agreement.
-For jointly authored works the signing author/presenter signs as authorized agent for the others.
- \end{enumerate}
-
-\end{boxedminipage}
-\caption{The author will be required to accept these conditions when they submit their paper via the web site.}
-\label{fig:fig02}
 \end{figure*}

### 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex
Update paper

@@
 \title{%
-Visualizing climate change mitigation and adaptation pathways\\																								% Line 1
+Simulation and visualization framework for decision making of climate mitigation  																								% Line 1
 %%% Please keep the \vspace{4pt} between lines in the title
 \vspace{4pt}
-for new urban development} 																																% Line 2 
+and adaptation strategies in new and existing urban development} 																																% Line 2 
 %If there is no second line then just put \phantom{Line 2} here
@@
 \begin{itemize}
-\item Intermingling of mitigation and adaptation strategies in a MACC.
-\item 
+\item Visualization of marginal abatement cost of urban scale building and energy system interventions.
+\item Intermingling of climate change mitigation and adaptation strategies in a decision making framework for development planning.
+\item The inclusion of embodied carbon as a metric in determining carbon emissions and marginal abatement cost.
 \end{itemize}
@@
 \section*{Practical Implications}
-Open-source simulation tools can be used to test the sensitivity of different decarbonisation and adaptation strategies for an urban area, alowwing planners better models to make planning decisions.
+Open-source simulation tools can be used to test the sensitivity of different decarbonisation and adaptation strategies for an urban area, allowing planners better models to make planning decisions.
 
@@
 
-Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, with recent estimates from global satellite observations placing the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C [ncdc].
+Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, while recent estimates from the \citet{ncdc} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990).
+This may not be considered a consistent level of \textit{global warming}, but it does point the dangerous warming trend facing human and non-human systems.
 Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems [X attribution science report for 2020].
-Implementing adaptation strategies within the built environment is necessary to increase social resilience and protect human life and prevent economic damage, perhaps even bolster both [X cobenefits of adaptation paper].
+Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above [X cobenefits of adaptation paper].
 Simultaneously, the mitigation of present emissions, the abatement of possible future emissions, and the sequestration of atmospheric carbon is necessary to curtail increasingly dangerous and catastrophic levels of warming.
 This process of carbon drawdown is very familiar within studies of the built environment with strategies posed for transportation, buildings, agriculture, forestry, and other landuses.
-MItigationa and adaptation strategies though are rarely, if ever simultaneously tested in building
+Mitigation and adaptation strategies though are rarely evaluated simultaneously in the context of urban development.
 
-In the presence of limited resources and a range of objectives, the cost and benefit of each strategy needs to be measured under a multitude of scenarios and in combination with other measures.
-This study will test the performance of adaptation and mitigation strategies alongside several development pathways and climate change scenarios for multiple population centers within BC.
+In the presence of limited resources and a range of objectives, the cost and benefit of proposed strategies need to be assessed on their own and while interacting with other strategies, as well as under the uncertainty of climate change and human action.
+The interaction of strategies is a key factor explored in \citet{rysanek MACC}, where exhaustive simulation of the possible strategies, depicted in Figure \ref{fig:sample_sequence}, is applied in the modeling of fifteen individual building retrofit strategies (a total of 32,768 unique combinations).
+From this database of simulated retrofits specific pathways for building retrofit can be generated.
+However, \citet{rysanek MACC} note that this process may not be desirable for every retrofit project that concerns only one building as the overhead cost of developing such a model is large and requires extensive computing resources.
+However, in the application of urban retrofit modeling for the purposes of enhancing policy making and incentive creation this framework could prove useful.
+
+Introducing the scale of a neighborhood or even entire city affords the use of an extensive modelling framework as described above, but further uncertainty is encountered in this problem space when considering urban development.
+No longer is the model concerned with answering a single question about a single existing building - how do we mitigate the most carbon at the lowest price?
+Now, the model is being applied in the context of an existing area where buildings and empty plots face a \textit{known-unknown} trajectory of new development, redevelopment, and no change.
+This brings in a the concept of a development timeline during which differing scales of development may occur.
+
+The resulting simulation database can be used to assess decarbonization pathways that align with development trajectories and/or different degrees of global warming.
+The difficulty though is in interpreting a large quantity of simulation data for its salience in the decarbonization and adaptation space.
+Several (\citep{various MACC papers}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point countered by \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework.
+Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.
+
+The literature on MACCs has not yet involved adaptation strategies as a form of emissions mitigation.
+However, as noted earlier adaptation and mitigation strategies ,may be decide upon fro the same funding perspective and therefore need to be considered together.
+Therefore this study integrates several adaptations strategies into the simulation process.
+These adaptation strategies are evaluated on the basis of marginal abatement cost, as well as their influence on the adaptation of the the development.
+Therefore mitigation strategies are equally evaluated as adaptations strategies.
+
+This study will test the performance of adaptation and mitigation strategies alongside one development pathway and two climate change pathways, simulated at two points in time (2050 and 2080), for a case study community in southwestern Canada; Wesbrook Village, Vancouver, British Columbia (BC).
+A baseline urban building energy model (UBEM) was created to represent the development of the community to-date, shown in Figure \ref{fig:wesbrook_base} alongside the future development and climate change pathways.
+
+\begin{figure}
+    \centering
+    \includegraphics{}
+    \caption{A sample of how }
+    \label{fig:sample_sequence}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{}
+    \caption{The baseline UBEM for Wesbrook Village in BC.}
+    \label{fig:wesbrook_base}
+\end{figure}
+
+\subsection*{Wesbrook Village} 
 Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
 
-Lastly, the outcomes of such studies need to be presented and interacted with well
+Wesbrook Village and the neighbouring Stadium Road are new communities that expected to reach 715,925 sqm.
+of residential floor space and 10,000 sqm.
+of non-residential floor space by 2040.
+It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{wesbrook plan; stadium plan}.
+The baseline for this study is taken at the end of 2020, where the development has completed its fifteenth year.
+The development, referred to throughout the study as \textit{Wesbrook}, is a compelling case study as it can be considered a model of medium-density new development for BC and North America at large.
+Building code for the community is modeled after the aspirational provincial code made more strict through a continuous review with the most recent version taking effect in January 2021 and targeting net-zero energy ready (NZER) by 2032; NZER buildings are built such that with the addition of solar panels or renewable technologies they would consume only as much energy as they produce.
+The energy system is a mixture of grid-connected systems, in building natural gas boilers, and a district heating system that supplies hydronic baseboard and floor heating systems as well as domestic hot water.
+This district heating system, described in \citet{McCarty 2021}, is designed to migrate from natural gas boilers to heat pumps fed by waste heat from a nearby particle accelerator facility that is trimmed up by peaking natural gas boilers.
+Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this is quickly becoming an obsolete design standard due to climate change \citep{ML cooling paper}.
+The intention with the code development for this community will however require cooling in buildings soon.
 
-\subsection*{}
+\subsubsection*{Retrofit and New Development Trajectory}
+The majority of Wesbrook has been completed as of 2020, with 50\% of the total expected build-out of 725,925 sqm.
+remaining between now and the mid-21st century.
+As indicated in Figure \ref{fig:wesbrook_base} the yet-to-be-completed development will be assessed in the model through the future periods.
+While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{Wesbrook masterplan}.
+The simulation framework is built from a baseline in 2020 of the completed development up to 2020.
+Two more time periods were simulated, the first in 2050 and then in 2080.
+The base-case for each time period assumes that the stock of buildings that were simulated in the previous time-step (existing) were retrofitted with similarly performing technologies and components.
+New buildings are however built to a performance profile modeled after the code trajectory referenced in Table \ref{tab:code_trajectory}.
+While it is expected that the future will hold more advanced technologies, code development is capped at the introduction of the NZER requirements.
+
+\begin{table*}[h]
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+    \caption{The first two-column table.}
+    \label{tab:code_trajectory}
+    \centering
+    \begin{tabular}{ | c | c | c | }
+        \hline
+        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
+        \hline
+        Entry 1 & Entry 2 & Entry 3 \\
+        \hline
+    \end{tabular}
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+\end{table*}
+
+\subsection*{Mitigation and adaptation decision tools}
+\citet{Rysanek MACC} expanded on the use of marginal abatement cost curves as a tool for planning retrofit pathways in single building optimization.
+The authors commentary was that by failing to consider technical and economic interactions MACCs such as those proposed by \citet{Mckinnsey} were inauthentic.
+Without accounting for the additionality of measures many MACCs fall into this grouping and limit their overall effectiveness.
+\citet{kesicki} acknowledges temporal interactions as an additional dimension that need to be considered when constructing MACCs.
+Traditionally MACCs were developed for annual-planning and more recently, as ambition has grown, so too have their temporal scales.
+These interactions can be summarized as understanding how investments made in the past may affect the outcome of the MACC, similar to the issue of technical and economic interactions.
+In planning buildings or infrastructure with MACCs this becomes a significant feature to consider as selecting investments to implement, one typically does so along an investment pathway.
+
+It is also of particular importance when developing infrastructure or buildings to consider the impact of a changing climate.
+Adaptation is prevalent in designing buildings in proximity to rising seas, adaptation ranges from hard to soft measures such as levies and dams to wetland restoration \citep{IPCC WGIIAR5 CH 15}.
+Evidence is pointing to the need to consider other impacts, such as overheating risk due to generally warmer days, nights with less cooling capacity, and more intense heat waves \citep{Lomas and Porrit; Rysanek ML Paper}.
+Measuring adaptation is a contentious field, as what defines successful adaptation is not as simple to calculate as net carbon emissions \citep{IPCC WGIIAR5 CH 14}.
+\citet{Brooks et al.} suggests several general criteria by which successful adaptation can be assessed: feasibility, efficacy/effectiveness, efficiency, acceptability/legitimacy, equity, and sustainability.
+The same authors also discuss the concept of Maladaptation, or the inadvertent increase in vulnerability to climate change as a result of development, which has equal importance to adaptation planning of buildings.
+For all criteria though, measures begin with assessing vulnerability of a subject to a stressor or collection of stressors.
+In the case of coastal development, a building's adaptive capacity and success can be measured by its vulnerability to increasingly intense sea level rise and storm surge.
+In the case of this study the stressor is heat gain and the vulnerability of a building to overheating.
+
+Metrics to evaluate adaptive capacity and ultimate effectiveness of measures are not concrete, as the metric typically has to be defined for the problem space \citep{brooks 2011}.
 
@@
 
-\subsection*{}
+\subsection*{Urban Building Energy Model}
+The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{CEA, Fonseca1, Fonseca2}.
+The CEA enables simulations of urban and neighborhood scale energy systems, as well as independently operating buildings.
+It is a hybrid dynamic statistical model that allows for efficient processing times, a necessity for large simulation sets such as the one in this study.
+
+The urban building energy model (UBEM) consists of a base-case of development and two future states of development, one in 2050 and another in 2080.
+The base-case was simulated once to tune the model.
+Each of the future states of development were simulated once for each combination of strategies under both climate change scenarios for a total of 1024 simulations.
+
+The UBEMs are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits, described in full in Table \ref{tab:model_parameters}.
+
+\begin{table}[ht]
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+    \caption{Example of a table.}
+    \label{tab:model_parameters}
+    \centering
+    \begin{tabular}{| c | c | c | }
+        \hline
+        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
+        \hline
+        Entry 1 & Entry 2 & Entry 3 \\
+        \hline
+    \end{tabular}
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+\end{table}
+
+\subsection*{Boundary conditions}
+The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{CWEC 2016 citation} was morphed, following the algorithms set out by \citet{Belcher} and expanded upon by \citet{CCworldweathergen}.
+These methods utilize the monthly delta of a region's between historical climate models and a projected pathway \citep{SSPs} to adjust the hourly values contained in an EPW file.
+Variations on the morphing process have been found, accounting for different shortcomings or the availability of more resolute climate model data to describe a region's specific topographic or climatic uniqueness that may not be captured in a typical climate model's often 100km x 100km grid.
+
+The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{CMIP6 text}.
+The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure.
+Morphed variables and ensemble composition is described in Table \ref{tab:model_table} The morphing process produced four morphed EPWs from two climate change pathways at two time periods, described in Figure \ref{fig:weatherfiles}.
+
+\subsection*{Strategies}
+Eight mitigation and adaptation strategies were selected to evaluate under the development pathways and climate change pathways.
+The strategies, show in Table \ref{tab:strategies}, reflect larger interventions into either existing buildings, new buildings, both, or the underlying energy system in the community.
+A strategy is implemented alone as well as in combination with the other seven to understand its range of potential impacts, which assists the decision-making framework in determining a pathway to implement strategies.
+
+\subsection*{Simulation}
+For each development period and under each climate change pathway the same eight strategies for decarbonization and adaptation to a changing climate were evaluated for their marginal cost of carbon abatement across the whole the Wesbrook development Strategies were tested on their own and in an exhaustive combination with the other seven strategies.
+The simulation procedure for each scenario began with the base-case, under which no strategies were implemented, following with 255 iterations where strategies where implemented alone and in combination with each other.
+This was repeated across both development pathways and both climate change pathways, leading to 1024 iterations of the model.
+The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration \citep{multithreading package}.
+At the time of writing radiation analysis was not able to be brought out of a single CPU core and thus steps were taken to minimize the amount of times the command was used as the processing time for the ~120 buildings in the UBEM was 25 minutes.
+In each scenario only 16 experiments required unique radiation profiles.
+These were run first in the loop of 256.
+The 240 simulations that followed then copied the appropriate output files from the radiation analysis.
+District heating primary energy requirement was modeled post-simulation as the system present in Wesbrook Village is nuanced to its efficiency and fuel source over the day.
+This process is described in the following section on "Operational and embodied carbon".
+
+A single entire simulation process (1024 iterations) required 64 hours of processing, utilizing 14 threads from an Intel i9-9900 8-core CPU at 4.6GHz, requiring 20GB of free RAM and an end storage requirement over 2TB of uncompressed results files.
+This detail is mentioned to help readers understand the scale of computing required to undertake simulations of this scale and to seek methods and functions that optimize processing times.
+
+\subsection*{Total Annualized Cost}
+Cost of components and technologies was gathered through several data sources, \citep{data sources for cost}.
+The authors recognize that cost is a highly uncertain data point to incorporate into building models.
+While the entire capital and operating cost of each building is not encompassed the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible.
+Cost is assessed as total annualized cost in \ref{eq:TAC}, where X is X, X is X, and X is X.
+
+\begin{equation}\label{eq:TAC}
+
+\end{equation}
+
+\subsection*{Operational and embodied carbon}
+Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service.
+BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{BC hydro methods}.
+The district heating provider intends for the system to fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and waste heat fed heat pumps will be created.
+This system was previously modelled in \citet{SRN paper}.
+Its carbon intensity was estimated to be between an annual average of XXXX and XXXX kgCO2e/kWh.
+The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps.
+Figure \ref{fig:district_heat_explainer} describes the modeled performance of the system.
+Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{CORIX infrastructure agreement}.
+
+The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{embodied carbon sources}, and are cradle-to-gate accounts of embodied carbon.
+The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.
+An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before reaching out for data from further away.
+
+\subsection*{Adaptation and mitigation}
+Mitigation was evaluated using the marginal cost of carbon abatement.
+Marginal abatement cost requires two metrics, the first being the net amount of carbon emitted between a base-case and some type of intervention and the net cost between the base-case and the intervention.
+In this study the base-case is the first iteration of the 256, where no strategies have been applied.
+Carbon emissions are calculated as the embodied carbon of capital expenditures (e.g.
+construction) and the 30-year operating carbon.
+Cost is the 30-year Total Annualized Cost, as described above.
+
+Adaptation was considered as the capacity of a building to remain in its comfort threshold while also mitigating carbon emissions.
+This is measured as the percent change from the baseline in total hours outside of the threshold for each iteration.
+For instance if in the baseline case total hours outside of threshold are 2000 and in an experiment the total hours outside of threshold are 1500, we have seen a 25\% decrease.
+
+\begin{table*}[h]
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+    \caption{A two-column table.}
+    \label{tab:model_table}
+    \centering
+    \begin{tabular}{| c | c | c | }
+        \hline
+        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
+        \hline
+        Entry 1 & Entry 2 & Entry 3 \\
+        \hline
+    \end{tabular}
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+\end{table*}
 
@@
 \section*{Results}
+The simulation procedure was executed for 1024 iterations, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building.
+For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic.
 
-\subsection*{}
+\subsection*{General Performance}
+Figure \ref{fig:joint_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios.
+Climate change does not appear to have a large impact on decarbonisation efforts.
+A warmer climate may even contribute to more emissions-performance at a lower cost.
+
+\subsection*{Visualizing decision making}
+Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
+For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto-front} highlights the best performing set of experiments.
+The charts are created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom most row which contains only a single strategy implemented.
+This presentation format allows us to view the optimal target and then evaluate how to achieve that by selecting strategy combinations in reverse, as suggested by the overlaid pathway.
+The lines in Figure \ref{fig:pareto-front} represent the set of optimal combinations for that particular group.
+In several cases no optimum set is reached due their only being one optimum.
+As a decision-making tool these types of graphs allow us to compare two base-metrics for economic decision making about mitigation and the effectiveness of the strategies as adaptation efforts.
+
+MACCs were drawn as another form of visualising decision making.
+Figure \ref{fig:MACC_budget} is drawn under the assumption that planners are expecting a worst-case climate change scenario by the end of the century, have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies.
+The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget.
+Another MACC was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
 

### 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
-For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto-front} highlights the best performing set of experiments.
+For each of the four combinations of development and climate change pathway, Figure \ref{fig:optimal_plots} highlights the best performing set of experiments.
 The charts are created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom most row which contains only a single strategy implemented.

### 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=1.0]{figures/general_results.eps}
+    \caption{General results from the iterations.}
+    \label{fig:joint_plot}
+\end{figure}
+
 \subsection*{Visualizing decision making}
@@
 
+\begin{figure*}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/optimal_plots.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:joint_plot}
+\end{figure*}
+
 MACCs were drawn as another form of visualising decision making.
-Figure \ref{fig:MACC_budget} is drawn under the assumption that planners are expecting a worst-case climate change scenario by the end of the century, have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies.
+Figure \ref{fig:MACC_budget} is drawn under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies.
 The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget.
 Another MACC was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
+A third MACC was generated under the assumption that planners would be interested in decarbonizing without abandoning the district heating system, the bulk of the emissions.
+
+To illustrate the construction of a more authentic MACC, we began with the combination of strategies that produced the best degree of adaptability under the worst-case climate change scenario at the end of the century, where the most hours outside of the comfort threshold were reduced.
+This strategy-set could have been any of those in Table \ref{tab:worst_case_adapt}.
 

### 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex
Text update

--- 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex
@@
 
+\begin{figure*}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/optimal_plots.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:pareto_plot}
+\end{figure*}
+
 MACCs were drawn as another form of visualising decision making.
-Figure \ref{fig:MACC_budget} is drawn under the assumption that planners are expecting a worst-case climate change scenario by the end of the century, have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies.
-The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget.
-Another MACC was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
+Figure \ref{fig:MACC_budget} is not a \textit{true} MACC in that you can only implement one of the bars.
+However, it improves on previous \textit{illustrative} MACCs in that the bars do not unnecessarily represent single strategy interventions, but rather a set of strategies.
+It was drawn to assist in planning under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies.
+The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting XXX.
+Another MACC, not \textit{true} was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
+
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/budget_macc.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:MACC_budget}
+\end{figure}
+
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/threshold_macc.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:MACC_budget}
+\end{figure}
+
+Two \textit{true} MACCs emerged in this study.
+The first represents a strategy-set that was chosen based on a high degree of adaptability present in, while also having a sizeable decrease in emissions.
+This was done under the worst-case climate scenario and the selected strategy-set (00011111) is highlighted in Figure \ref{fig:pareto_plot}.
+Figure \ref{fig:MACC_true_noDH_waterfall} describes how each strategy contributes to the overall decrease in emissions.
+The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction.
+This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity.
+The Figure has been altered in the vertical and horizontal access to then compare the scale of the remaining reduction measures, as only three measures actually contribute to emissions reductions.
+This point will be returned to more in the discussion, but raises that question about affordable marginal cost for significant abatement after fuel-switching has been achieved.
+This scenario only achieves 45\% emissions reduction over the baseline by 2080.
+
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=1]{figures/true_macc_noDH_waterfall.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:MACC_true_noDH_waterfall}
+\end{figure}
+
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/true_macc_noDH.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:MACC_true_noDH}
+\end{figure}
+
+A second \textit{true} MACC was generated under to abate as many emissions as possible under the assumption that the district heating system could not be abandoned and assuming the worst-case climate scenario.
+Figure \ref{fig:MACC_true_DH_waterfall} describes how each measure contributes to overall emissions reduction.
+
+\begin{figure*}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/true_macc_dh.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:MACC_true_DH}
+\end{figure*}
+
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=1]{figures/true_macc_dh_waterfall.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:MACC_true_DH_waterfall}
+\end{figure}
 

### 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics{}
-    \caption{A sample of how }
+    \includegraphics{figures/sample_sequence.eps}
+    \caption{Each scenario iterated through 256 combinations of strategy implementation.}
     \label{fig:sample_sequence}
@@
 
-\begin{table*}[h]
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-    \caption{A two-column table.}
-    \label{tab:model_table}
-    \centering
-    \begin{tabular}{| c | c | c | }
-        \hline
-        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
-        \hline
-        Entry 1 & Entry 2 & Entry 3 \\
-        \hline
-    \end{tabular}
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-\end{table*}
-
 %---------------------------------------------------------------------------------------
@@
 This point will be returned to more in the discussion, but raises that question about affordable marginal cost for significant abatement after fuel-switching has been achieved.
-This scenario only achieves 45\% emissions reduction over the baseline by 2080.
+This scenario only achieves 67\% emissions reduction over the baseline by 2080.
 
@@
 Figure \ref{fig:MACC_true_DH_waterfall} describes how each measure contributes to overall emissions reduction.
+The resulting MACC shows a more consistent scale of MAC and overall abatement between measures, but total abatement is only 8\% of the baseline's emissions.
 
@@
     \centering
-    \includegraphics[scale=1]{figures/true_macc_dh_waterfall.eps}
+    \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
@@
 \section*{Discussion}
+The use of MACCs, \textit{true} and \textit{illustrative}, offers urban scale energy and development planning a way to compare different types of interventions for their merit as adaptation and mitigation interventions.
+This analysis is robust in that it simulates the technical and financial interaction of the proposed strategies under multiple climate change pathways and following different development trajectories.
+The first limitation lies in the not-so-explicit temporal interaction of the interventions.
+Each building was modeled as having its own unique construction and retrofit dates, which contribute to the emissions and total annualized cost profile for each run of the district energy model.
+While unique in their start and end date they are all set on a 30year time horizon for all elements replacement.
+While for some building technologies this may be a realistic time horizon for design-life, for many others it is not.
+Future efforts need to consider equipment and technology replacements more actively while also engaging the temporal simulation steps at more fine scales, possibly ten-years.
 
-\subsection*{}
+\subsection*{Strategy choice}
+A major limitation is the framework underpinning this study is the finite space of strategy choice.
+We test eight strategies here that are applied generally across the district.
+Future efforts need to be more precise with strategy implementation based on building or site need.
+
+\subsection*{Abatement after fuel-switching}
+- possible solutions
+- non economic frameworks
+
+The context for this study sets up an interesting proposition within BC.
+The electrical grid is majority hydroelectric.
+Emissions within the building sector are therefore driven by natural gas use, either on site or within district systems.
+As the two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition the use of natural gas must be eliminated.
+
+This however raises the point of how abatement should continua once the significant reductions are made and systems are then relying on a near-carbon free grid.
+This study showed in testing rooftop photovoltaic that for this type of density, just rooftop panels are not going to generate significant amounts of energy or contribute to emissions reductions; in the worst-case climate scenario rooftop panels reduced emissions by 4.4\%.
 

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics{figures/sample_sequence.eps}
+    \includegraphics[scale=2.3]{figures/sample_sequence.eps}
     \caption{Each scenario iterated through 256 combinations of strategy implementation.}
@@
 The base-case for each time period assumes that the stock of buildings that were simulated in the previous time-step (existing) were retrofitted with similarly performing technologies and components.
-New buildings are however built to a performance profile modeled after the code trajectory referenced in Table \ref{tab:code_trajectory}.
+New buildings are however built to a performance profile modeled after the changes in the municipalities building performance code (\citep{REAP}).
 While it is expected that the future will hold more advanced technologies, code development is capped at the introduction of the NZER requirements.
 
-\begin{table*}[h]
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-    \caption{The first two-column table.}
-    \label{tab:code_trajectory}
-    \centering
-    \begin{tabular}{ | c | c | c | }
-        \hline
-        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
-        \hline
-        Entry 1 & Entry 2 & Entry 3 \\
-        \hline
-    \end{tabular}
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-\end{table*}
+% \begin{table*}[h]
+%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+%     \caption{The first two-column table.}
+%     \label{tab:code_trajectory}
+%     \centering
+%     \begin{tabular}{ | c | c | c | }
+%         \hline
+%         \bf{Year} & \bf{Code Name} 2 & \bf{Performance Note} \\
+%         \hline
+%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
+%         \hline
+%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
+%         \hline
+%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
+%         \hline
+%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
+%         \hline
+%     \end{tabular}
+%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+% \end{table*}
 
@@
 
-The UBEMs are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits, described in full in Table \ref{tab:model_parameters}.
+The UBEMs are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits.
 
-\begin{table}[ht]
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-    \caption{Example of a table.}
-    \label{tab:model_parameters}
-    \centering
-    \begin{tabular}{| c | c | c | }
-        \hline
-        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
-        \hline
-        Entry 1 & Entry 2 & Entry 3 \\
-        \hline
-    \end{tabular}
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-\end{table}
+% \begin{table}[ht]
+%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+%     \caption{Example of a table.}
+%     \label{tab:model_parameters}
+%     \centering
+%     \begin{tabular}{| c | c | c | }
+%         \hline
+%         \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
+%         \hline
+%         Entry 1 & Entry 2 & Entry 3 \\
+%         \hline
+%     \end{tabular}
+%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+% \end{table}
 
@@
 For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic.
+From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, \ref{fig:MACC_true_noDH}, and \ref{fig:MACC_true_DH}.
+These are discussed at more in the following sections but differ in that they are constructed following two logics.
+The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected.
+The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in Figures \ref{fig:MACC_true_noDH_waterfall} and \ref{fig:MACC_true_DH_waterfall}.
+
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=1]{figures/budget_macc.eps}
+    \caption{Illustrative MACC made assuming a budget of \$11 million in net cost was permitted for any plotted strategy-set.}
+    \label{fig:MACC_budget}
+\end{figure}
+
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=1]{figures/threshold_macc.eps}
+    \caption{Illustrative MACC made assuming an emissions reduction threshold of 80\% was necessary for any plotted strategy-set.}
+    \label{fig:MACC_threshold}
+\end{figure}
 
 \subsection*{General Performance}
-Figure \ref{fig:joint_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios.
+Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios.
 Climate change does not appear to have a large impact on decarbonisation efforts.
@@
     \includegraphics[scale=1.0]{figures/general_results.eps}
-    \caption{General results from the iterations.}
-    \label{fig:joint_plot}
+    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
+    \label{fig:cross_plot}
 \end{figure}
@@
 
-\begin{figure*}[hbpt]
-    \centering
-    \includegraphics[scale=0.8]{figures/optimal_plots.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:pareto_plot}
-\end{figure*}
-
 MACCs were drawn as another form of visualising decision making.
@@
 The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting XXX.
-Another MACC, not \textit{true} was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
-
-\begin{figure}[hbpt]
-    \centering
-    \includegraphics[scale=0.8]{figures/budget_macc.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:MACC_budget}
-\end{figure}
-
-\begin{figure}[hbpt]
-    \centering
-    \includegraphics[scale=0.8]{figures/threshold_macc.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:MACC_budget}
-\end{figure}
+Another \textit{illustrative} MACC was drawn, seen in Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
 
@@
 \end{figure}
+
+\begin{figure*}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/optimal_plots.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:pareto_plot}
+\end{figure*}
 

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
 This may not be considered a consistent level of \textit{global warming}, but it does point the dangerous warming trend facing human and non-human systems.
-Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems [X attribution science report for 2020].
-Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above [X cobenefits of adaptation paper].
+Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems \citep{Frame et al.}.
+Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above \citep{ Schünemann}.
 Simultaneously, the mitigation of present emissions, the abatement of possible future emissions, and the sequestration of atmospheric carbon is necessary to curtail increasingly dangerous and catastrophic levels of warming.
@@
 The difficulty though is in interpreting a large quantity of simulation data for its salience in the decarbonization and adaptation space.
-Several (\citep{various MACC papers}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point countered by \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework.
+Several (\citep{afsahri; ibhrahim}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework.
 Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.
@@
 \citet{Rysanek MACC} expanded on the use of marginal abatement cost curves as a tool for planning retrofit pathways in single building optimization.
-The authors commentary was that by failing to consider technical and economic interactions MACCs such as those proposed by \citet{Mckinnsey} were inauthentic.
+The authors commentary was that by failing to consider technical and economic interactions MACCs such as those proposed by \citet{Mckinnsey} were more \textit{illustrative} than planning tools.
 Without accounting for the additionality of measures many MACCs fall into this grouping and limit their overall effectiveness.
@@
 \subsection*{Boundary conditions}
-The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{CWEC 2016 citation} was morphed, following the algorithms set out by \citet{Belcher} and expanded upon by \citet{CCworldweathergen}.
-These methods utilize the monthly delta of a region's between historical climate models and a projected pathway \citep{SSPs} to adjust the hourly values contained in an EPW file.
+The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{CWEC 2016 citation} was morphed, following the algorithms set out by \citet{Belcher} and expanded upon by \citet{jentsch}.
+These methods utilize the monthly delta of a region's between historical climate models and a projected pathway \citep{oneil kreiglar} to adjust the hourly values contained in an EPW file.
 Variations on the morphing process have been found, accounting for different shortcomings or the availability of more resolute climate model data to describe a region's specific topographic or climatic uniqueness that may not be captured in a typical climate model's often 100km x 100km grid.
 
-The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{CMIP6 text}.
+The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{oneil tebaldi}.
 The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure.
@@
 This was repeated across both development pathways and both climate change pathways, leading to 1024 iterations of the model.
-The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration \citep{multithreading package}.
+The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration \citep{mckerns}.
 At the time of writing radiation analysis was not able to be brought out of a single CPU core and thus steps were taken to minimize the amount of times the command was used as the processing time for the ~120 buildings in the UBEM was 25 minutes.
@@
 \subsection*{Total Annualized Cost}
-Cost of components and technologies was gathered through several data sources, \citep{data sources for cost}.
+Cost of components and technologies was gathered through several data sources, \citep{rs means; corix cpcn; ctbuh 3for2; kegal; salasobich}.
 The authors recognize that cost is a highly uncertain data point to incorporate into building models.
@@
 
-The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{embodied carbon sources}, and are cradle-to-gate accounts of embodied carbon.
+The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{ec3, ICE db, Rodriguez Droguett, Rodriguez}, and are cradle-to-gate accounts of embodied carbon.
 The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 
-Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, while recent estimates from the \citet{ncdc} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990).
+Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, while recent estimates from the \citet{} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990).
 This may not be considered a consistent level of \textit{global warming}, but it does point the dangerous warming trend facing human and non-human systems.
-Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems \citep{Frame et al.}.
-Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above \citep{ Schünemann}.
+Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems \citep{frame_climate_2020,frame_economic_2020}.
+Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above \citep{schunemann_mitigation_2020}.
 Simultaneously, the mitigation of present emissions, the abatement of possible future emissions, and the sequestration of atmospheric carbon is necessary to curtail increasingly dangerous and catastrophic levels of warming.
@@
 In the presence of limited resources and a range of objectives, the cost and benefit of proposed strategies need to be assessed on their own and while interacting with other strategies, as well as under the uncertainty of climate change and human action.
-The interaction of strategies is a key factor explored in \citet{rysanek MACC}, where exhaustive simulation of the possible strategies, depicted in Figure \ref{fig:sample_sequence}, is applied in the modeling of fifteen individual building retrofit strategies (a total of 32,768 unique combinations).
+The interaction of strategies is a key factor explored in \citet{rysanek_using_2013}, where exhaustive simulation of the possible strategies, depicted in Figure \ref{fig:sample_sequence}, is applied in the modeling of fifteen individual building retrofit strategies (a total of 32,768 unique combinations).
 From this database of simulated retrofits specific pathways for building retrofit can be generated.
-However, \citet{rysanek MACC} note that this process may not be desirable for every retrofit project that concerns only one building as the overhead cost of developing such a model is large and requires extensive computing resources.
+However, \citet{rysanek_using_2013} note that this process may not be desirable for every retrofit project that concerns only one building as the overhead cost of developing such a model is large and requires extensive computing resources.
 However, in the application of urban retrofit modeling for the purposes of enhancing policy making and incentive creation this framework could prove useful.
@@
 The difficulty though is in interpreting a large quantity of simulation data for its salience in the decarbonization and adaptation space.
-Several (\citep{afsahri; ibhrahim}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework.
+Several (\citep{}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki_marginal_nodate} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework.
 Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.
@@
 \bibliographystyle{BS2021}
-\bibliography{references}
+\bibliography{bs2021_ref}
 \newpage

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 The difficulty though is in interpreting a large quantity of simulation data for its salience in the decarbonization and adaptation space.
-Several (\citep{}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki_marginal_nodate} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework.
+Several (\citep{afshari_life-cycle_2014,ibrahim_methodology_2016}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki_marginal_nodate} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek_using_2013} through an underlying sequential and exhaustive simulation framework.
 Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.
@@
 of non-residential floor space by 2040.
-It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{wesbrook plan; stadium plan}.
+It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{ubc_planning_ubc_2020,ubc_planning_ubc_2020_SR}.
 The baseline for this study is taken at the end of 2020, where the development has completed its fifteenth year.
@@
 The energy system is a mixture of grid-connected systems, in building natural gas boilers, and a district heating system that supplies hydronic baseboard and floor heating systems as well as domestic hot water.
-This district heating system, described in \citet{McCarty 2021}, is designed to migrate from natural gas boilers to heat pumps fed by waste heat from a nearby particle accelerator facility that is trimmed up by peaking natural gas boilers.
-Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this is quickly becoming an obsolete design standard due to climate change \citep{ML cooling paper}.
+This district heating system, described in \citet{mccarty_accepted_2020}, is designed to migrate from natural gas boilers to heat pumps fed by waste heat from a nearby particle accelerator facility that is trimmed up by peaking natural gas boilers.
+Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this is quickly becoming an obsolete design standard due to climate change \citep{rysanek_forecasting_2021}.
 The intention with the code development for this community will however require cooling in buildings soon.
@@
 As indicated in Figure \ref{fig:wesbrook_base} the yet-to-be-completed development will be assessed in the model through the future periods.
-While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{Wesbrook masterplan}.
+While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{noauthor_ubc_2020_wb}.
 The simulation framework is built from a baseline in 2020 of the completed development up to 2020.
@@
 The base-case for each time period assumes that the stock of buildings that were simulated in the previous time-step (existing) were retrofitted with similarly performing technologies and components.
-New buildings are however built to a performance profile modeled after the changes in the municipalities building performance code (\citep{REAP}).
+New buildings are however built to a performance profile modeled after the changes in the municipalities building performance code (\citep{noauthor_residential_2021}).
 While it is expected that the future will hold more advanced technologies, code development is capped at the introduction of the NZER requirements.
@@
 \subsection*{Mitigation and adaptation decision tools}
-\citet{Rysanek MACC} expanded on the use of marginal abatement cost curves as a tool for planning retrofit pathways in single building optimization.
-The authors commentary was that by failing to consider technical and economic interactions MACCs such as those proposed by \citet{Mckinnsey} were more \textit{illustrative} than planning tools.
+\citet{rysanek_using_2013} expanded on the use of marginal abatement cost curves as a tool for planning retrofit pathways in single building optimization.
+The authors commentary was that by failing to consider technical and economic interactions MACCs such as those proposed by \citet{mckinsey__co_climate_2010} were more \textit{illustrative} than planning tools.
 Without accounting for the additionality of measures many MACCs fall into this grouping and limit their overall effectiveness.
-\citet{kesicki} acknowledges temporal interactions as an additional dimension that need to be considered when constructing MACCs.
+\citet{kesicki_marginal_nodate} acknowledges temporal interactions as an additional dimension that need to be considered when constructing MACCs.
 Traditionally MACCs were developed for annual-planning and more recently, as ambition has grown, so too have their temporal scales.
@@
 It is also of particular importance when developing infrastructure or buildings to consider the impact of a changing climate.
-Adaptation is prevalent in designing buildings in proximity to rising seas, adaptation ranges from hard to soft measures such as levies and dams to wetland restoration \citep{IPCC WGIIAR5 CH 15}.
+Adaptation is prevalent in designing buildings in proximity to rising seas, adaptation ranges from hard to soft measures such as levies and dams to wetland restoration \citep{}.
 Evidence is pointing to the need to consider other impacts, such as overheating risk due to generally warmer days, nights with less cooling capacity, and more intense heat waves \citep{Lomas and Porrit; Rysanek ML Paper}.

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
 \usepackage{subcaption}
+
+\usepackage{tabularx}
 %-----------------------------SET SKIP SPACES -------------------------------------------------------------------
@@
 At present mitigation and adaptations strategies compete for constrained resources within a future of uncertain climate impacts.
-Meeting decarbonisation goals while implementing robust and resilient adaptions strategies requires an analysis structure that can account for uncertainty as well as depict how the intermingling of strategies may hinder or benefit the ultimate trajectory of actions.
+Meeting decarbonisation goals while implementing robust and resilient adaptation strategies requires an analysis structure that can account for uncertainty as well as depict how the intermingling of strategies may hinder or benefit the ultimate trajectory of actions.
 The marginal abatement cost curve (MACC) is an indispensable tool for planning mitigation pathways, but has historically not relied upon robust experimental analysis making it notional at best nor has it included a view of adaptation pathways.
-This study utilizes a recently developed and nearly finished medium-density community in Vancouver, British Columbia, Canada of 15,000 residents as a case study for developing a pathway based MACC.
+This study utilizes a newly developed and nearly finished medium-density community in Vancouver, British Columbia, Canada of 15,000 residents as a case study for developing a pathway based MACC.
 Multiple mitigation and adaptation measures are modeled individually and through exhaustive combination to test their sensitivity on marginal abatement cost and residual cost of climate change.
-The resulting MACCs are compared with more tradition decision support visualizations to argue for a more comprehensive approach to decarbonisation and adaptation planning.
+Several visualizations are created to demonstrate several ways of analyzing the resulting large set of data.
 
@@
 \item The inclusion of embodied carbon as a metric in determining carbon emissions and marginal abatement cost.
+\item Contribution of an open-dataset of simulated demand, cost, and emissions for use in reanalysis and further studies.
 \end{itemize}
@@
 \section*{Practical Implications}
-Open-source simulation tools can be used to test the sensitivity of different decarbonisation and adaptation strategies for an urban area, allowing planners better models to make planning decisions.
+Open-source simulation tools can be used to test the sensitivity of different decarbonisation and adaptation strategies for an urban area, allowing planners better models to make well-informed planning decisions.
+The resulting visualizations of this study offer a sample of this, as well as an example of a comprehensive urban building energy model.
+The results also raise questions about decarbonization pathways in British Columbia after strategies such as fuel switching are implemented, reducing the majority of emissions, but not entirely creating zero-carbon communities.
 
@@
 
-Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, while recent estimates from the \citet{} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990).
-This may not be considered a consistent level of \textit{global warming}, but it does point the dangerous warming trend facing human and non-human systems.
-Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems \citep{frame_climate_2020,frame_economic_2020}.
+Atmospheric concentrations of carbon dioxide are just over 410 parts per million, while recent estimates from the \citet{noauthor_state_2020} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990).
+This may not be considered a consistent level of \textit{global warming}, but it does indicate a the dangerous warming trend facing human and non-human systems.
+Climate change impacts are now being recognized as burdens on economic and social systems \citep{frame_climate_2020}.
 Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above \citep{schunemann_mitigation_2020}.
@@
 In the presence of limited resources and a range of objectives, the cost and benefit of proposed strategies need to be assessed on their own and while interacting with other strategies, as well as under the uncertainty of climate change and human action.
-The interaction of strategies is a key factor explored in \citet{rysanek_using_2013}, where exhaustive simulation of the possible strategies, depicted in Figure \ref{fig:sample_sequence}, is applied in the modeling of fifteen individual building retrofit strategies (a total of 32,768 unique combinations).
-From this database of simulated retrofits specific pathways for building retrofit can be generated.
+The interaction of strategies is a key factor explored in \citet{rysanek_using_2013}, where exhaustive simulation is applied in the modeling of fifteen individual building retrofit strategies (a total of 32,768 unique combinations).
+From this, a database of simulated retrofits specific pathways for a single building can be generated.
 However, \citet{rysanek_using_2013} note that this process may not be desirable for every retrofit project that concerns only one building as the overhead cost of developing such a model is large and requires extensive computing resources.
@@
 Now, the model is being applied in the context of an existing area where buildings and empty plots face a \textit{known-unknown} trajectory of new development, redevelopment, and no change.
-This brings in a the concept of a development timeline during which differing scales of development may occur.
+This brings in the concept of a development timeline during which differing scales of development may occur.
 
 The resulting simulation database can be used to assess decarbonization pathways that align with development trajectories and/or different degrees of global warming.
-The difficulty though is in interpreting a large quantity of simulation data for its salience in the decarbonization and adaptation space.
-Several (\citep{afshari_life-cycle_2014,ibrahim_methodology_2016}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki_marginal_nodate} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek_using_2013} through an underlying sequential and exhaustive simulation framework.
+The difficulty though is in interpreting a large quantity of simulation data for its salience in the mitigation and adaptation planning space.
+Several have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki_marginal_2012} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek_using_2013} through an underlying sequential and exhaustive simulation framework \citep{afshari_life-cycle_2014,ibrahim_methodology_2016}.
 Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.
@@
 The literature on MACCs has not yet involved adaptation strategies as a form of emissions mitigation.
-However, as noted earlier adaptation and mitigation strategies ,may be decide upon fro the same funding perspective and therefore need to be considered together.
+However, as noted earlier adaptation and mitigation strategies, may be decided upon from the same funding perspective and therefore need to be considered together.
 Therefore this study integrates several adaptations strategies into the simulation process.
-These adaptation strategies are evaluated on the basis of marginal abatement cost, as well as their influence on the adaptation of the the development.
-Therefore mitigation strategies are equally evaluated as adaptations strategies.
+These adaptation strategies are evaluated on the basis of marginal abatement cost, as well as their influence on adaptation within the development.
+Therefore, mitigation strategies are equally evaluated as adaptations strategies.
 
-This study will test the performance of adaptation and mitigation strategies alongside one development pathway and two climate change pathways, simulated at two points in time (2050 and 2080), for a case study community in southwestern Canada; Wesbrook Village, Vancouver, British Columbia (BC).
+This study will test the performance of eight strategies alongside one development pathway and two climate change pathways, simulated at two points in time (2050 and 2080), for a case study community in southwestern Canada; Wesbrook Village, Vancouver, British Columbia (BC).
 A baseline urban building energy model (UBEM) was created to represent the development of the community to-date, shown in Figure \ref{fig:wesbrook_base} alongside the future development and climate change pathways.
@@
 \subsection*{Wesbrook Village} 
-Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
+Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty, diagrammed in Figure \ref{fig:sample_sequence}.
 
@@
 of non-residential floor space by 2040.
-It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{ubc_planning_ubc_2020,ubc_planning_ubc_2020_SR}.
+It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}.
 The baseline for this study is taken at the end of 2020, where the development has completed its fifteenth year.
@@
 The energy system is a mixture of grid-connected systems, in building natural gas boilers, and a district heating system that supplies hydronic baseboard and floor heating systems as well as domestic hot water.
-This district heating system, described in \citet{mccarty_accepted_2020}, is designed to migrate from natural gas boilers to heat pumps fed by waste heat from a nearby particle accelerator facility that is trimmed up by peaking natural gas boilers.
-Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this is quickly becoming an obsolete design standard due to climate change \citep{rysanek_forecasting_2021}.
-The intention with the code development for this community will however require cooling in buildings soon.
+This district heating system, described in the context of a UBEM in \citet{mccarty_accepted_2020}, is designed to switch from natural gas boilers to heat pumps amplified by waste heat from a nearby particle accelerator facility but still with peaking boilers fueled by natural gas.
+Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this may become an obsolete design standard due to climate change \citep{rysanek_forecasting_2021}.
+The intention with the code development for this community is that cooling will be required within a decade \citep{noauthor_residential_2021}.
 
@@
 As indicated in Figure \ref{fig:wesbrook_base} the yet-to-be-completed development will be assessed in the model through the future periods.
-While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{noauthor_ubc_2020_wb}.
+While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{ubc_planning_ubc_2020_wb}.
 The simulation framework is built from a baseline in 2020 of the completed development up to 2020.
@@
 Without accounting for the additionality of measures many MACCs fall into this grouping and limit their overall effectiveness.
-\citet{kesicki_marginal_nodate} acknowledges temporal interactions as an additional dimension that need to be considered when constructing MACCs.
+\citet{kesicki_marginal_2012} acknowledges temporal interactions as an additional dimension that need to be considered when constructing MACCs.
 Traditionally MACCs were developed for annual-planning and more recently, as ambition has grown, so too have their temporal scales.
@@
 It is also of particular importance when developing infrastructure or buildings to consider the impact of a changing climate.
-Adaptation is prevalent in designing buildings in proximity to rising seas, adaptation ranges from hard to soft measures such as levies and dams to wetland restoration \citep{}.
-Evidence is pointing to the need to consider other impacts, such as overheating risk due to generally warmer days, nights with less cooling capacity, and more intense heat waves \citep{Lomas and Porrit; Rysanek ML Paper}.
-Measuring adaptation is a contentious field, as what defines successful adaptation is not as simple to calculate as net carbon emissions \citep{IPCC WGIIAR5 CH 14}.
-\citet{Brooks et al.} suggests several general criteria by which successful adaptation can be assessed: feasibility, efficacy/effectiveness, efficiency, acceptability/legitimacy, equity, and sustainability.
-The same authors also discuss the concept of Maladaptation, or the inadvertent increase in vulnerability to climate change as a result of development, which has equal importance to adaptation planning of buildings.
+Adaptation is prevalent in designing buildings in proximity to rising seas, with strategies ranging from hard measures such as levies and dams to soft measures such as wetland restoration \citep{mimura_adaptation_nodate}.
+Evidence is pointing to the need to consider other impacts, such as overheating risk due to generally warmer days, nights with less cooling capacity, and more intense heat waves \citep{lomas_overheating_2017,rysanek_forecasting_2021}.
+Measuring adaptation is a contentious field, as what defines successful adaptation is not as simple to calculate as net carbon emissions \citep{noble_adaptation_2014}.
+\citet{brooks_tracking_2011} suggests several general criteria by which successful adaptation can be assessed: feasibility, efficacy/effectiveness, efficiency, acceptability/legitimacy, equity, and sustainability.
+The same authors also discuss the concept of \textit{Maladaptation}, or the inadvertent increase in vulnerability to climate change as a result of development, which has equal importance to adaptation planning of buildings.
 For all criteria though, measures begin with assessing vulnerability of a subject to a stressor or collection of stressors.
@@
 
-Metrics to evaluate adaptive capacity and ultimate effectiveness of measures are not concrete, as the metric typically has to be defined for the problem space \citep{brooks 2011}.
-
 %---------------------------------------------------------------------------------------
@@
 
+\begin{table*}[ht]
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+    \caption{Each strategy as it was applied in the simulations.}
+    \footnotesize
+    \label{tab:strategies}
+    \centering
+    \begin{tabularx}{\textwidth}{|X|X|X|}
+        \hline
+        \bf{Strategy} & \bf{Description} & \bf{Scale} \\
+        \hline
+        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings \\
+        \hline
+        Green Roof & Install green roofs for insulative, albedo, and heat gain benefits. & All Buildings \\
+        \hline
+        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings \\
+        \hline
+        Passive House & Require passive house building codes for envelope. & New Buildings \\
+        \hline
+        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings \\
+        \hline
+        Mass Timber & Construction must utilize mass timber. & New Buildings \\
+        \hline
+        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings \\
+        \hline
+        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings \\
+        \hline
+    \end{tabularx}
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+\end{table*}
+
 \subsection*{Urban Building Energy Model}
-The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{CEA, Fonseca1, Fonseca2}.
+The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{fonseca_integrated_2015,fonseca_city_2016,the_cea_team_city_2020}.
 The CEA enables simulations of urban and neighborhood scale energy systems, as well as independently operating buildings.
 It is a hybrid dynamic statistical model that allows for efficient processing times, a necessity for large simulation sets such as the one in this study.
+These urban building energy models (UBEM) are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits.
 
-The urban building energy model (UBEM) consists of a base-case of development and two future states of development, one in 2050 and another in 2080.
+The UBEMs consists of a base-case of development and two future states of development, one in 2050 and another in 2080.
 The base-case was simulated once to tune the model.
@@
 
-The UBEMs are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits.
-
-% \begin{table}[ht]
-%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-%     \caption{Example of a table.}
-%     \label{tab:model_parameters}
-%     \centering
-%     \begin{tabular}{| c | c | c | }
-%         \hline
-%         \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
-%         \hline
-%         Entry 1 & Entry 2 & Entry 3 \\
-%         \hline
-%     \end{tabular}
-%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-% \end{table}
-
 \subsection*{Boundary conditions}
-The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{CWEC 2016 citation} was morphed, following the algorithms set out by \citet{Belcher} and expanded upon by \citet{jentsch}.
-These methods utilize the monthly delta of a region's between historical climate models and a projected pathway \citep{oneil kreiglar} to adjust the hourly values contained in an EPW file.
+The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{cwec_2016} was morphed, following the algorithms set out by \citet{belcher_constructing_2005} and expanded upon by \citet{jentsch_climate_2008}.
+For a variable such as temperature being morphed, the monthly delta of a region's historical climate models and a future climate model is calculated to apply to one of several morphing algorithms to adjust the hourly values contained in an EPW file.
 Variations on the morphing process have been found, accounting for different shortcomings or the availability of more resolute climate model data to describe a region's specific topographic or climatic uniqueness that may not be captured in a typical climate model's often 100km x 100km grid.
 
-The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{oneil tebaldi}.
+The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{oneill_scenario_2016}.
 The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure.
-Morphed variables and ensemble composition is described in Table \ref{tab:model_table} The morphing process produced four morphed EPWs from two climate change pathways at two time periods, described in Figure \ref{fig:weatherfiles}.
+Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios.
+These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
+defined in \citet{oneill_roads_2017}. The four morphed EPWs are described in Figure \ref{fig:weatherfiles}.
 
@@
 Eight mitigation and adaptation strategies were selected to evaluate under the development pathways and climate change pathways.
-The strategies, show in Table \ref{tab:strategies}, reflect larger interventions into either existing buildings, new buildings, both, or the underlying energy system in the community.
+The strategies, described in Table \ref{tab:strategies}, reflect larger interventions into either existing buildings, new buildings, both, or the underlying energy system in the community.
 A strategy is implemented alone as well as in combination with the other seven to understand its range of potential impacts, which assists the decision-making framework in determining a pathway to implement strategies.
@@
 \subsection*{Simulation}
-For each development period and under each climate change pathway the same eight strategies for decarbonization and adaptation to a changing climate were evaluated for their marginal cost of carbon abatement across the whole the Wesbrook development Strategies were tested on their own and in an exhaustive combination with the other seven strategies.
+For each development period and under each climate change pathway the same eight strategies for carbon mitigation and climate change adaptation to a changing climate were evaluated for their marginal cost of carbon abatement across the whole the Wesbrook development.
 The simulation procedure for each scenario began with the base-case, under which no strategies were implemented, following with 255 iterations where strategies where implemented alone and in combination with each other.
 This was repeated across both development pathways and both climate change pathways, leading to 1024 iterations of the model.
-The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration \citep{mckerns}.
+The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration.
 At the time of writing radiation analysis was not able to be brought out of a single CPU core and thus steps were taken to minimize the amount of times the command was used as the processing time for the ~120 buildings in the UBEM was 25 minutes.
@@
 These were run first in the loop of 256.
+This is due to some strategies not influencing the radiation simulation output, such as in the \textit{Mass Timber} case.
 The 240 simulations that followed then copied the appropriate output files from the radiation analysis.
@@
 \subsection*{Total Annualized Cost}
-Cost of components and technologies was gathered through several data sources, \citep{rs means; corix cpcn; ctbuh 3for2; kegal; salasobich}.
+Components and technology costs was gathered through several data sources, \citep{noauthor_cpcn_2014,schlueter_3for2_2016,salasovich_energy_2016,kegel_life_nodate,gordian_rsmeans_2020}.
 The authors recognize that cost is a highly uncertain data point to incorporate into building models.
 While the entire capital and operating cost of each building is not encompassed the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible.
-Cost is assessed as total annualized cost in \ref{eq:TAC}, where X is X, X is X, and X is X.
-
-\begin{equation}\label{eq:TAC}
-
-\end{equation}
+Cost is assessed as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.
 
@@
 Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service.
-BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{BC hydro methods}.
+BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}.
 The district heating provider intends for the system to fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and waste heat fed heat pumps will be created.
-This system was previously modelled in \citet{SRN paper}.
-Its carbon intensity was estimated to be between an annual average of XXXX and XXXX kgCO2e/kWh.
+This system was previously modelled in \citet{mccarty_accepted_2020}.
+Its carbon intensity was estimated to be between an annual average of 10.8 and 180.0 kgCO2e/kWh.
 The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps.
-Figure \ref{fig:district_heat_explainer} describes the modeled performance of the system.
-Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{CORIX infrastructure agreement}.
+Figure \ref{fig:district_heat_explainer} describes a baseline case of performance with the system.
+Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.
 
-The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{ec3, ICE db, Rodriguez Droguett, Rodriguez}, and are cradle-to-gate accounts of embodied carbon.
+The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,rodriguez_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
 The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.
-An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before reaching out for data from further away.
+An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.
 
@@
 Mitigation was evaluated using the marginal cost of carbon abatement.
-Marginal abatement cost requires two metrics, the first being the net amount of carbon emitted between a base-case and some type of intervention and the net cost between the base-case and the intervention.
+Marginal abatement cost requires two metrics, the first being the net amount of carbon emitted between a base-case and scenario and the net cost between the base-case and scenario.
 In this study the base-case is the first iteration of the 256, where no strategies have been applied.
-Carbon emissions are calculated as the embodied carbon of capital expenditures (e.g.
-construction) and the 30-year operating carbon.
-Cost is the 30-year Total Annualized Cost, as described above.
+Carbon emissions are calculated as the embodied carbon of capital expenditures and the 30-year operating carbon.
+Cost is the 30-year TAC.
 
 Adaptation was considered as the capacity of a building to remain in its comfort threshold while also mitigating carbon emissions.
-This is measured as the percent change from the baseline in total hours outside of the threshold for each iteration.
-For instance if in the baseline case total hours outside of threshold are 2000 and in an experiment the total hours outside of threshold are 1500, we have seen a 25\% decrease.
+The threshold is set to setpoints of the buildings, which are in a majority 21C for heating and 26C for cooling - except where changed by the first strategy.
+The deviation from the threshold is measured as the percent change from the baseline in \textit{total hours outside of the threshold} for each iteration.
+For instance if in the baseline case \textit{total hours outside of threshold} are 2000 and in an experiment the \textit{total hours outside of threshold} are 1500, we have seen a 25\% decrease.
 
@@
 \section*{Results}
-The simulation procedure was executed for 1024 iterations, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building.
+The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building.
 For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic.
+A final open-database is available in the repository mentioned in the abstract.
 From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, \ref{fig:MACC_true_noDH}, and \ref{fig:MACC_true_DH}.
@@
 Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios.
-Climate change does not appear to have a large impact on decarbonisation efforts.
-A warmer climate may even contribute to more emissions-performance at a lower cost.
+Three groups tend to emerge with the most start difference being that one group is emitting far more than the other two.
+This is a result of those scenarios still relying on the natural-gas based heating system.
+This difference is apparent across both climate change pathways, leading to a conslusion that the impacts of more severe climate are not disrupting mitigation efforts in the model.
+It appears to enable it to an extent.
+Comparing the highlighted groups of similar scenarios between the best-case and worst-case scenarios a decrease in lifetime emissions is apparent.
+We suspect that this is due to the warmer temperatures reducing the heating seasons as well as enabling the district to remain below the heat pump capacity more of the year.
+Figure \ref{fig:comapre_district} shows this in the operation of the district in the baseline cases from each climate scenario.
 
@@
 Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
-For each of the four combinations of development and climate change pathway, Figure \ref{fig:optimal_plots} highlights the best performing set of experiments.
-The charts are created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom most row which contains only a single strategy implemented.
-This presentation format allows us to view the optimal target and then evaluate how to achieve that by selecting strategy combinations in reverse, as suggested by the overlaid pathway.
-The lines in Figure \ref{fig:pareto-front} represent the set of optimal combinations for that particular group.
+For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier.
+The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%.
+The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented.
+This format allows us to view the optimal target and then evaluate how to achieve that by selecting strategy combinations in reverse, as suggested by the overlaid pathway.
 In several cases no optimum set is reached due their only being one optimum.
@@
 MACCs were drawn as another form of visualising decision making.
-Figure \ref{fig:MACC_budget} is not a \textit{true} MACC in that you can only implement one of the bars.
+Figure \ref{fig:MACC_budget} is not a \textit{true} MACC in that you can only implement one of the strategy-sets, represented by the bars.
 However, it improves on previous \textit{illustrative} MACCs in that the bars do not unnecessarily represent single strategy interventions, but rather a set of strategies.
 It was drawn to assist in planning under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies.
-The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting XXX.
+The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting \textit{01011001} at the marginal abatement cost of -\$123.
 Another \textit{illustrative} MACC was drawn, seen in Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
+All bars represet strategy-sets that would reach that reductions total, ultimately \textit{0111000} is chosen at the marginal abatement cost of -\$50.
 
-Two \textit{true} MACCs emerged in this study.
-The first represents a strategy-set that was chosen based on a high degree of adaptability present in, while also having a sizeable decrease in emissions.
-This was done under the worst-case climate scenario and the selected strategy-set (00011111) is highlighted in Figure \ref{fig:pareto_plot}.
+Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions.
+This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}.
 Figure \ref{fig:MACC_true_noDH_waterfall} describes how each strategy contributes to the overall decrease in emissions.
-The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction.
+The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction.
 This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity.
-The Figure has been altered in the vertical and horizontal access to then compare the scale of the remaining reduction measures, as only three measures actually contribute to emissions reductions.
-This point will be returned to more in the discussion, but raises that question about affordable marginal cost for significant abatement after fuel-switching has been achieved.
+The majority of the abatement can be attributed to the heat pump strategy, removing natural gas from the fuel mix, while the other strategies can be said to lending to adaptability.
+This point about the fuel mix will be returned to more in the discussion, but raises that question about how to affordably meet zero-carbon targets after fuel-switching has been achieved.
 This scenario only achieves 67\% emissions reduction over the baseline by 2080.
@@
 
-A second \textit{true} MACC was generated under to abate as many emissions as possible under the assumption that the district heating system could not be abandoned and assuming the worst-case climate scenario.
+A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario.
 Figure \ref{fig:MACC_true_DH_waterfall} describes how each measure contributes to overall emissions reduction.
-The resulting MACC shows a more consistent scale of MAC and overall abatement between measures, but total abatement is only 8\% of the baseline's emissions.
+The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.
 
@@
 \section*{Discussion}
-The use of MACCs, \textit{true} and \textit{illustrative}, offers urban scale energy and development planning a way to compare different types of interventions for their merit as adaptation and mitigation interventions.
+The use of MACCs, \textit{true} and \textit{illustrative}, offers urban scale energy and development planners a way to compare different types of interventions for their merit as adaptation and mitigation interventions.
 This analysis is robust in that it simulates the technical and financial interaction of the proposed strategies under multiple climate change pathways and following different development trajectories.
@@
 Each building was modeled as having its own unique construction and retrofit dates, which contribute to the emissions and total annualized cost profile for each run of the district energy model.
-While unique in their start and end date they are all set on a 30year time horizon for all elements replacement.
-While for some building technologies this may be a realistic time horizon for design-life, for many others it is not.
+While unique in their start and end date they are all set on a 30-year time horizon for all elements replacement.
+For some building technologies this may be a realistic time horizon for design-life, for many others it is not.
 Future efforts need to consider equipment and technology replacements more actively while also engaging the temporal simulation steps at more fine scales, possibly ten-years.
@@
 \subsection*{Strategy choice}
-A major limitation is the framework underpinning this study is the finite space of strategy choice.
+A major limitation in the framework underpinning this study is the finite space of strategy choice.
 We test eight strategies here that are applied generally across the district.
+This may not always be a problem if prior to the study a strategy evaluation study is conducted or subject-matter experts are brought in to help establish priors.
 Future efforts need to be more precise with strategy implementation based on building or site need.
@@
 \subsection*{Abatement after fuel-switching}
-- possible solutions
-- non economic frameworks
-
 The context for this study sets up an interesting proposition within BC.
@@
 Emissions within the building sector are therefore driven by natural gas use, either on site or within district systems.
-As the two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition the use of natural gas must be eliminated.
+The two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition the use of natural gas must be eliminated.
+This however raises the point of how abatement should continua once the significant reductions are made and systems are then relying on a near-carbon free grid.
+Future building code intends for new buildings to be net-zero \textit{energy} ready, but this study showed in testing rooftop photovoltaic that for this type of density, just rooftop panels are not going to generate significant amounts of energy or contribute to emissions reductions; in the worst-case climate scenario rooftop panels alone reduced emissions by 4.4\%.
 
-This however raises the point of how abatement should continua once the significant reductions are made and systems are then relying on a near-carbon free grid.
-This study showed in testing rooftop photovoltaic that for this type of density, just rooftop panels are not going to generate significant amounts of energy or contribute to emissions reductions; in the worst-case climate scenario rooftop panels reduced emissions by 4.4\%.
+Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016, zeitz_comparing_2019}.
+This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.
 
@@
 \section*{Conclusion}
+In this study the output of 1024 different urban building energy simulations was discussed in the context of use marginal abatement cost curves and complimentary visualizations to make decisions regarding mitigation and adaptation planning for a medium-density community in Vancouver, British Columbia.
+The simulations were differing combinations of development completeness of the community, climate change pathway (between best- and worst-case scenarios), and eight mitigation and adaptation strategies.
+
+The resulting MACCs were created from two perspectives.
+First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) provide general guidance on choosing sets of strategies to achieve mitigation under different planning constraints.
+The \textit{true} MACCs (Figures \ref{fig:MACC_true_DH} and \ref{fig:MACC_true_noDH}) reveal how the individual strategies within a set interact to technically and financially to ultimately abate a certain amount of carbon.
+The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria using a plot of pareto optimums (Figure \ref{fig:pareto_plot}).
+This enables planners to begin to assess adaptation targets alongside abatement.
+
+The analysis had limitations discussed in the literature on using MACCs for decision-support.
+These include being more realistic about building technology and component lifetimes, which requires the framework to consider retirement.
+As well the study is constrained by computational resources and known mitigation and adaptation strategies for the site.
+Future studies should seek to better understand either through exploratory analysis or expert elicitation, which strategies are reasonable for the market and context.
+This will also aide in developing a cost and carbon database.
+
+The results of the simulation provide more than an example for decision-support visualization.
+In comparing the results we see a large difference in abatement between systems that continue to rely on natural gas into the latter half of the century and those that transition to a hydroelectric fed grid.
+The large jump between the two provokes the thought of how deep emissions reductions will be achieved when demand from space heating, cooling, DHW, and plug load are being met by affordable near-zero carbon electricity.
 

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 \usepackage{subcaption}
-
 \usepackage{tabularx}
@@
 It is also of particular importance when developing infrastructure or buildings to consider the impact of a changing climate.
-Adaptation is prevalent in designing buildings in proximity to rising seas, with strategies ranging from hard measures such as levies and dams to soft measures such as wetland restoration \citep{mimura_adaptation_nodate}.
+Adaptation is prevalent in designing buildings in proximity to rising seas, with strategies ranging from hard measures such as levies and dams to soft measures such as wetland restoration \citep{pachauri_climate_2015}.
 Evidence is pointing to the need to consider other impacts, such as overheating risk due to generally warmer days, nights with less cooling capacity, and more intense heat waves \citep{lomas_overheating_2017,rysanek_forecasting_2021}.
-Measuring adaptation is a contentious field, as what defines successful adaptation is not as simple to calculate as net carbon emissions \citep{noble_adaptation_2014}.
+Measuring adaptation is a contentious field, as what defines successful adaptation is not as simple to calculate as net carbon emissions \citep{pachauri_climate_2015}.
 \citet{brooks_tracking_2011} suggests several general criteria by which successful adaptation can be assessed: feasibility, efficacy/effectiveness, efficiency, acceptability/legitimacy, equity, and sustainability.
@@
 
-\begin{figure}[hbpt]
+\begin{figure*}
 \centering
-    \includegraphics[scale=1]{figures/budget_macc.eps}
+\begin{minipage}[b]{.45\textwidth}
+    \hspace*{-1.05cm}\includegraphics[scale=1.0]{figures/budget_macc.eps}
     \caption{Illustrative MACC made assuming a budget of \$11 million in net cost was permitted for any plotted strategy-set.}
     \label{fig:MACC_budget}
-\end{figure}
-
-\begin{figure}[hbpt]
-    \centering
-    \includegraphics[scale=1]{figures/threshold_macc.eps}
+\end{minipage}\qquad
+\begin{minipage}[b]{.45\textwidth}
+    \hspace*{-.4cm}\includegraphics[scale=1.0]{figures/threshold_macc.eps}
     \caption{Illustrative MACC made assuming an emissions reduction threshold of 80\% was necessary for any plotted strategy-set.}
     \label{fig:MACC_threshold}
-\end{figure}
+\end{minipage}
+\end{figure*}
 
@@
 This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}.
-Figure \ref{fig:MACC_true_noDH_waterfall} describes how each strategy contributes to the overall decrease in emissions.
+Figure \ref{fig:MACC_true_noDH} describes how each strategy contributes to the overall decrease in emissions.
 The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction.
@@
 
-\begin{figure}[hbpt]
+% \begin{figure}[hbpt]
+%     \centering
+%     \includegraphics[scale=1]{figures/true_macc_noDH_waterfall.eps}
+%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+%     \label{fig:MACC_true_noDH_waterfall}
+% \end{figure}
+
+% \begin{figure}[hbpt]
+%     \centering
+%     \includegraphics[scale=0.8]{figures/true_macc_noDH.eps}
+%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+%     \label{fig:MACC_true_noDH}
+% \end{figure}
+
+\begin{figure}[t]
     \centering
-    \includegraphics[scale=1]{figures/true_macc_noDH_waterfall.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:MACC_true_noDH_waterfall}
-\end{figure}
-
-\begin{figure}[hbpt]
-    \centering
-    \includegraphics[scale=0.8]{figures/true_macc_noDH.eps}
+    \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
@@
 A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario.
-Figure \ref{fig:MACC_true_DH_waterfall} describes how each measure contributes to overall emissions reduction.
+Figure \ref{fig:MACC_true_DH} describes how each measure contributes to overall emissions reduction.
 The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.
 
-\begin{figure*}[hbpt]
+% \begin{figure*}[hbpt]
+%     \centering
+%     \includegraphics[scale=0.8]{figures/true_macc_dh.eps}
+%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+%     \label{fig:MACC_true_DH}
+% \end{figure*}
+
+% \begin{figure}[hbpt]
+%     \centering
+%     \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
+%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+%     \label{fig:MACC_true_DH_waterfall}
+% \end{figure}
+
+\begin{figure}[t]
     \centering
-    \includegraphics[scale=0.8]{figures/true_macc_dh.eps}
+    \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
     \label{fig:MACC_true_DH}
-\end{figure*}
-
-\begin{figure}[hbpt]
-    \centering
-    \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:MACC_true_DH_waterfall}
 \end{figure}
@@
 \bibliography{bs2021_ref}
-\newpage
-\onecolumn
-Please \textbf{do not} include this disclaimer in your paper.  You will be required to accept these conditions when you  submit your paper via the web site.
-
-\begin{figure*}[ht]
-\centering
-
-\end{figure*}
-
+% \newpage
+% \onecolumn
+% Please \textbf{do not} include this disclaimer in your paper.  You will be required to accept these conditions when you  submit your paper via the web site.
 \end{document}

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
 
-\begin{figure}
-    \centering
-    \includegraphics[scale=2.3]{figures/sample_sequence.eps}
-    \caption{Each scenario iterated through 256 combinations of strategy implementation.}
-    \label{fig:sample_sequence}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[scale=1.5]{figures/sample_sequence.eps}
+%     \caption{Each scenario iterated through 256 combinations of strategy implementation.}
+%     \label{fig:sample_sequence}
+% \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics{}
-    \caption{The baseline UBEM for Wesbrook Village in BC.}
-    \label{fig:wesbrook_base}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics{}
+%     \caption{The baseline UBEM for Wesbrook Village in BC.}
+%     \label{fig:wesbrook_base}
+% \end{figure}
 
@@
 
-\begin{figure}[hbpt]
+\begin{figure}[hbt]
     \centering
-    \includegraphics[scale=1.0]{figures/general_results.eps}
+    \includegraphics[scale=0.8]{figures/general_results_box.eps}
     \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
@@
 
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=0.8]{figures/true_maccs_waterfalls_both.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:true_macc_both}
+\end{figure}
+
 Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions.
@@
 
-% \begin{figure}[hbpt]
+% \begin{figure}[t]
 %     \centering
-%     \includegraphics[scale=1]{figures/true_macc_noDH_waterfall.eps}
-%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-%     \label{fig:MACC_true_noDH_waterfall}
-% \end{figure}
-
-% \begin{figure}[hbpt]
-%     \centering
-%     \includegraphics[scale=0.8]{figures/true_macc_noDH.eps}
+%     \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
 %     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
@@
 % \end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:MACC_true_noDH}
-\end{figure}
 
@@
 
-% \begin{figure*}[hbpt]
+% \begin{figure}[t]
 %     \centering
-%     \includegraphics[scale=0.8]{figures/true_macc_dh.eps}
+%     \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
 %     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
 %     \label{fig:MACC_true_DH}
-% \end{figure*}
-
-% \begin{figure}[hbpt]
-%     \centering
-%     \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
-%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-%     \label{fig:MACC_true_DH_waterfall}
 % \end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:MACC_true_DH}
-\end{figure}
 
@@
 %---------------------------------------------------------------------------------------
-This document is a summary of various documents from previous Building Simulation Conferences.
-%here starts the references
+\footnotesize
 \bibliographystyle{BS2021}

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 This study will test the performance of eight strategies alongside one development pathway and two climate change pathways, simulated at two points in time (2050 and 2080), for a case study community in southwestern Canada; Wesbrook Village, Vancouver, British Columbia (BC).
-A baseline urban building energy model (UBEM) was created to represent the development of the community to-date, shown in Figure \ref{fig:wesbrook_base} alongside the future development and climate change pathways.
+A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.
 
@@
 \subsection*{Wesbrook Village} 
-Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty, diagrammed in Figure \ref{fig:sample_sequence}.
-
+% Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
 Wesbrook Village and the neighbouring Stadium Road are new communities that expected to reach 715,925 sqm.
@@
 \subsection*{Urban Building Energy Model}
-The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{fonseca_integrated_2015,fonseca_city_2016,the_cea_team_city_2020}.
+The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{fonseca_city_2016,the_cea_team_city_2020}.
 The CEA enables simulations of urban and neighborhood scale energy systems, as well as independently operating buildings.
@@
 
-The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{oneill_scenario_2016}.
+The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models.
 The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure.
@@
 
-The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,rodriguez_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
+The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
 The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.
@@
     \centering
+    \captionsetup{margin=.5cm}
     \includegraphics[scale=0.8]{figures/general_results_box.eps}
@@
     \centering
-    \includegraphics[scale=0.8]{figures/true_maccs_waterfalls_both.eps}
+    \captionsetup{margin=.5cm}
+    \includegraphics[scale=0.95]{figures/true_maccs_waterfalls_both.eps}
     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
@@
 
-\begin{figure*}[hbpt]
+% \begin{figure*}[hbpt]
+%     \centering
+%     \includegraphics[scale=0.8]{figures/optimal_plots.eps}
+%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+%     \label{fig:pareto_plot}
+% \end{figure*}
+
+\begin{figure}[hbpt]
     \centering
-    \includegraphics[scale=0.8]{figures/optimal_plots.eps}
+    \includegraphics[scale=0.55]{figures/pareto_plots_585.eps}
     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
     \label{fig:pareto_plot}
-\end{figure*}
+\end{figure}
 
@@
 
-Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016, zeitz_comparing_2019}.
+Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}.
 This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 A final open-database is available in the repository mentioned in the abstract.
-From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, \ref{fig:MACC_true_noDH}, and \ref{fig:MACC_true_DH}.
+From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}.
 These are discussed at more in the following sections but differ in that they are constructed following two logics.
 The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected.
-The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in Figures \ref{fig:MACC_true_noDH_waterfall} and \ref{fig:MACC_true_DH_waterfall}.
+The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in the first and third frame of Figure \ref{fig:true_macc_both}.
 
@@
 This is a result of those scenarios still relying on the natural-gas based heating system.
-This difference is apparent across both climate change pathways, leading to a conslusion that the impacts of more severe climate are not disrupting mitigation efforts in the model.
+This difference is apparent across both climate change pathways, leading to a conclusion that the impacts of more severe climate are not disrupting mitigation efforts in the model.
 It appears to enable it to an extent.
-Comparing the highlighted groups of similar scenarios between the best-case and worst-case scenarios a decrease in lifetime emissions is apparent.
+Comparing the highlighted groups of similar strategy-sets between the best-case and worst-case scenarios a decrease in lifetime emissions is apparent.
 We suspect that this is due to the warmer temperatures reducing the heating seasons as well as enabling the district to remain below the heat pump capacity more of the year.
-Figure \ref{fig:comapre_district} shows this in the operation of the district in the baseline cases from each climate scenario.
+
+% Figure \ref{fig:comapre_district} shows this in the operation of the district in the baseline cases from each climate scenario.
 
@@
 \subsection*{Visualizing decision making}
-Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
-For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier.
-The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%.
-The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented.
-This format allows us to view the optimal target and then evaluate how to achieve that by selecting strategy combinations in reverse, as suggested by the overlaid pathway.
-In several cases no optimum set is reached due their only being one optimum.
-As a decision-making tool these types of graphs allow us to compare two base-metrics for economic decision making about mitigation and the effectiveness of the strategies as adaptation efforts.
-
 MACCs were drawn as another form of visualising decision making.
@@
 
+Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
+For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier.
+The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%.
+The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented.
+These charts can inform the creation of a \textit{true} MACC by informing which strategy set is chosen based on not only marginal abatement cost, but also the adaptation metric.
+
 Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions.
 This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}.
-Figure \ref{fig:MACC_true_noDH} describes how each strategy contributes to the overall decrease in emissions.
-The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction.
+Figure \ref{fig:true_macc_both} describes how each strategy contributes to the overall decrease in emissions.
+The MACC is shown in Figure \ref{fig:true_macc_both} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction.
 This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity.
@@
 A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario.
-Figure \ref{fig:MACC_true_DH} describes how each measure contributes to overall emissions reduction.
+Figure \ref{fig:true_macc_both} describes how each measure contributes to overall emissions reduction.
 The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.
@@
 
-\begin{figure}[hbpt]
+\begin{figure}[t]
     \centering
-    \includegraphics[scale=0.55]{figures/pareto_plots_585.eps}
+    \captionsetup{margin=.5cm}
+    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
@@
 First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) provide general guidance on choosing sets of strategies to achieve mitigation under different planning constraints.
-The \textit{true} MACCs (Figures \ref{fig:MACC_true_DH} and \ref{fig:MACC_true_noDH}) reveal how the individual strategies within a set interact to technically and financially to ultimately abate a certain amount of carbon.
+The \textit{true} MACCs (Figure \ref{fig:true_macc_both}) reveal how the individual strategies within a set interact to technically and financially to ultimately abate a certain amount of carbon.
 The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria using a plot of pareto optimums (Figure \ref{fig:pareto_plot}).

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
 \section*{Results}
-The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building.
-For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic.
-A final open-database is available in the repository mentioned in the abstract.
-From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}.
-These are discussed at more in the following sections but differ in that they are constructed following two logics.
-The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected.
-The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in the first and third frame of Figure \ref{fig:true_macc_both}.
+\begin{figure}[hbpt]
+    \centering
+    \captionsetup{margin=.5cm}
+    \includegraphics[scale=0.8]{figures/general_results_box.eps}
+    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
+    \label{fig:cross_plot}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}[hbpt]
+    \centering
+    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
+    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios.
+The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
+    \label{fig:compare_district}
+\end{figure}
+
+\begin{figure*}[hbpt]
 \centering
@@
 
+The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building.
+For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic.
+A final open-database is available in the repository mentioned in the abstract.
+From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}.
+These are discussed at more in the following sections but differ in that they are constructed following two logics.
+The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected.
+The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in the first and third frame of Figure \ref{fig:true_macc_both}.
+
 \subsection*{General Performance}
@@
 We suspect that this is due to the warmer temperatures reducing the heating seasons as well as enabling the district to remain below the heat pump capacity more of the year.
-
-% Figure \ref{fig:comapre_district} shows this in the operation of the district in the baseline cases from each climate scenario.
-
-\begin{figure}[hbt]
-    \centering
-    \captionsetup{margin=.5cm}
-    \includegraphics[scale=0.8]{figures/general_results_box.eps}
-    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
-    \label{fig:cross_plot}
-\end{figure}
+Figure \ref{fig:compare_district} shows this in the operation of the district in the baseline cases from each climate scenario
 

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
 \title{%
-Simulation and visualization framework for decision making of climate mitigation  																								% Line 1
-%%% Please keep the \vspace{4pt} between lines in the title
-\vspace{4pt}
-and adaptation strategies in new and existing urban development} 																																% Line 2 
+Simulation and visualization framework for selecting appropriate urban-scale climate mitigation and adaptation strategies} 																																% Line 2 
 %If there is no second line then just put \phantom{Line 2} here
@@
 The marginal abatement cost curve (MACC) is an indispensable tool for planning mitigation pathways, but has historically not relied upon robust experimental analysis making it notional at best nor has it included a view of adaptation pathways.
-This study utilizes a newly developed and nearly finished medium-density community in Vancouver, British Columbia, Canada of 15,000 residents as a case study for developing a pathway based MACC.
+This study utilizes a newly developed, medium-density residential community in Vancouver, British Columbia, Canada (15,000 residents) as a case study for developing a pathway-based MACC.
 Multiple mitigation and adaptation measures are modeled individually and through exhaustive combination to test their sensitivity on marginal abatement cost and residual cost of climate change.
@@
 Atmospheric concentrations of carbon dioxide are just over 410 parts per million, while recent estimates from the \citet{noauthor_state_2020} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990).
-This may not be considered a consistent level of \textit{global warming}, but it does indicate a the dangerous warming trend facing human and non-human systems.
+This may not be considered a consistent level of \textit{global warming}, but it does indicate a dangerous warming trend facing human and non-human systems.
 Climate change impacts are now being recognized as burdens on economic and social systems \citep{frame_climate_2020}.
@@
 Simultaneously, the mitigation of present emissions, the abatement of possible future emissions, and the sequestration of atmospheric carbon is necessary to curtail increasingly dangerous and catastrophic levels of warming.
-This process of carbon drawdown is very familiar within studies of the built environment with strategies posed for transportation, buildings, agriculture, forestry, and other landuses.
+This process of carbon drawdown is very familiar within studies of the built environment with strategies posed for transportation, buildings, agriculture, forestry, and other land-uses.
 Mitigation and adaptation strategies though are rarely evaluated simultaneously in the context of urban development.
@@
 The interaction of strategies is a key factor explored in \citet{rysanek_using_2013}, where exhaustive simulation is applied in the modeling of fifteen individual building retrofit strategies (a total of 32,768 unique combinations).
-From this, a database of simulated retrofits specific pathways for a single building can be generated.
-However, \citet{rysanek_using_2013} note that this process may not be desirable for every retrofit project that concerns only one building as the overhead cost of developing such a model is large and requires extensive computing resources.
-However, in the application of urban retrofit modeling for the purposes of enhancing policy making and incentive creation this framework could prove useful.
+From this, a database of simulated retrofit-specific pathways for a single building can be generated.
 
-Introducing the scale of a neighborhood or even entire city affords the use of an extensive modelling framework as described above, but further uncertainty is encountered in this problem space when considering urban development.
-No longer is the model concerned with answering a single question about a single existing building - how do we mitigate the most carbon at the lowest price?
-Now, the model is being applied in the context of an existing area where buildings and empty plots face a \textit{known-unknown} trajectory of new development, redevelopment, and no change.
+Introducing the scale of a neighborhood or even entire city requires a more extensive modelling framework as described above, as well as the consideration of additional sources of model uncertainty attributed to urban-scale matters.
+No longer would a model be concerned with answering a single question about a single existing building - how do we mitigate the most carbon at the lowest price?
+Now, the model would  being applied in the context of an existing area where buildings and empty plots could face a \textit{known-unknown} trajectory of either new development, redevelopment, and no change.
 This brings in the concept of a development timeline during which differing scales of development may occur.
 
-The resulting simulation database can be used to assess decarbonization pathways that align with development trajectories and/or different degrees of global warming.
-The difficulty though is in interpreting a large quantity of simulation data for its salience in the mitigation and adaptation planning space.
-Several have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki_marginal_2012} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek_using_2013} through an underlying sequential and exhaustive simulation framework \citep{afshari_life-cycle_2014,ibrahim_methodology_2016}.
-Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.
+This study integrates several climate adaptation strategies into the urban-scale energy simulation process.
+Adaptation strategies are evaluated on the basis of marginal costs of mitigation \textit{and} adaptation, vis-a-vis the influence of individual design strategies on the resilience of the urban development to expectec climate change.
 
-The literature on MACCs has not yet involved adaptation strategies as a form of emissions mitigation.
-However, as noted earlier adaptation and mitigation strategies, may be decided upon from the same funding perspective and therefore need to be considered together.
-Therefore this study integrates several adaptations strategies into the simulation process.
-These adaptation strategies are evaluated on the basis of marginal abatement cost, as well as their influence on adaptation within the development.
-Therefore, mitigation strategies are equally evaluated as adaptations strategies.
+This study will simulate the performance of eight climate mitigation and adaptation strategies alongside one urban development trajectory and two climate change scenarios.
+The simulations will be also carried out at two individual time periods (2050 and 2080), for a case study community in southwestern Canada: Wesbrook Village, Vancouver, British Columbia (BC).
+A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.
 
-This study will test the performance of eight strategies alongside one development pathway and two climate change pathways, simulated at two points in time (2050 and 2080), for a case study community in southwestern Canada; Wesbrook Village, Vancouver, British Columbia (BC).
-A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.
+The outline of this study is as follows. SecitonXX does..... Seciton XX does....
 
@@
 % Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
-Wesbrook Village and the neighbouring Stadium Road are new communities that expected to reach 715,925 sqm.
-of residential floor space and 10,000 sqm.
-of non-residential floor space by 2040.
-It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}.
-The baseline for this study is taken at the end of 2020, where the development has completed its fifteenth year.
+Wesbrook Village is a new residential community under construction by the University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}.
+On it completion within the next decade, the community will provide permanent housing for over 25,000 residents of Vancouver, BC primarily in mid-rise (4-6 stories) and high-rise residential towers (15-30 stories).
+
  The development, referred to throughout the study as \textit{Wesbrook}, is a compelling case study as it can be considered a model of medium-density new development for BC and North America at large.
-Building code for the community is modeled after the aspirational provincial code made more strict through a continuous review with the most recent version taking effect in January 2021 and targeting net-zero energy ready (NZER) by 2032; NZER buildings are built such that with the addition of solar panels or renewable technologies they would consume only as much energy as they produce.
-The energy system is a mixture of grid-connected systems, in building natural gas boilers, and a district heating system that supplies hydronic baseboard and floor heating systems as well as domestic hot water.
-This district heating system, described in the context of a UBEM in \citet{mccarty_accepted_2020}, is designed to switch from natural gas boilers to heat pumps amplified by waste heat from a nearby particle accelerator facility but still with peaking boilers fueled by natural gas.
-Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this may become an obsolete design standard due to climate change \citep{rysanek_forecasting_2021}.
-The intention with the code development for this community is that cooling will be required within a decade \citep{noauthor_residential_2021}.
+For example, Wesbrook was developed under the auspices of a progressive building code, overseen by UBC, that targets all new campus residential developments to satisfy net-zero energy ready (NZER) performance levels by 2032.
+
+ Buildings of the Wesbrook community make use of mix of energy systems.
+Some buildings provide space heating using hydronic in-floor radiant systems; some provide space heating via electric baseboard heaters.
+Some buildings operate dedicated boilers for generating hot water; other buildings receive hot water from a natural gas-fired district energy system.
+This district heating system is described in the context of a UBEM in \citet{mccarty_accepted_2020}.
+Centralized space cooling has not been provided for across the development, but concerns around the potential need for future space cooling is a growing concern for naturally-ventilated buildings in the region \citep{rysanek_forecasting_2021}.
+With its current building codes, UBC does intend that space cooling may be a required energy service in the community in the next decade \citep{noauthor_residential_2021}.
 
@@
 The majority of Wesbrook has been completed as of 2020, with 50\% of the total expected build-out of 725,925 sqm.
-remaining between now and the mid-21st century.
+remaining to be constructed.
 As indicated in Figure \ref{fig:wesbrook_base} the yet-to-be-completed development will be assessed in the model through the future periods.
-While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{ubc_planning_ubc_2020_wb}.
+The Wesbrook planning and development scheme is well laid out in master-planning documents \citep{ubc_planning_ubc_2020_wb}.
 The simulation framework is built from a baseline in 2020 of the completed development up to 2020.
-Two more time periods were simulated, the first in 2050 and then in 2080.
+Two more time periods are simulated, the first in 2050 and then in 2080.
 The base-case for each time period assumes that the stock of buildings that were simulated in the previous time-step (existing) were retrofitted with similarly performing technologies and components.
-New buildings are however built to a performance profile modeled after the changes in the municipalities building performance code (\citep{noauthor_residential_2021}).
-While it is expected that the future will hold more advanced technologies, code development is capped at the introduction of the NZER requirements.
+New buildings are however built to a performance profile modeled after expected changes in the community's building performance code (\citep{noauthor_residential_2021}).
 
@@
 
-\subsection*{Urban Building Energy Model}
+\subsection*{Urban Building Energy Model (UBEM)}
 The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{fonseca_city_2016,the_cea_team_city_2020}.
 The CEA enables simulations of urban and neighborhood scale energy systems, as well as independently operating buildings.
-It is a hybrid dynamic statistical model that allows for efficient processing times, a necessity for large simulation sets such as the one in this study.
-These urban building energy models (UBEM) are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits.
 
-The UBEMs consists of a base-case of development and two future states of development, one in 2050 and another in 2080.
+The constructed UBEM consists of a base-case of development and two future states of development, one in 2050 and another in 2080.
 The base-case was simulated once to tune the model.
@@
 
-\subsection*{Boundary conditions}
 The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{cwec_2016} was morphed, following the algorithms set out by \citet{belcher_constructing_2005} and expanded upon by \citet{jentsch_climate_2008}.
-For a variable such as temperature being morphed, the monthly delta of a region's historical climate models and a future climate model is calculated to apply to one of several morphing algorithms to adjust the hourly values contained in an EPW file.
-Variations on the morphing process have been found, accounting for different shortcomings or the availability of more resolute climate model data to describe a region's specific topographic or climatic uniqueness that may not be captured in a typical climate model's often 100km x 100km grid.
-
-The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models.
-The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure.
 Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios.
 These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
-defined in \citet{oneill_roads_2017}. The four morphed EPWs are described in Figure \ref{fig:weatherfiles}.
+defined in \citet{oneill_roads_2017}. Four morphed climate files are produced and described in Figure \ref{fig:weatherfiles}.
 
-\subsection*{Strategies}
+\subsection*{Climate mitigation and adaptation strategies}
 Eight mitigation and adaptation strategies were selected to evaluate under the development pathways and climate change pathways.
@@
 
+Adaptation was considered as the capacity of a building to remain in its comfort threshold while also mitigating carbon emissions.
+The threshold is set to setpoints of the buildings, which are in a majority 21C for heating and 26C for cooling - except where changed by the first strategy.
+The deviation from the threshold is measured as the percent change from the baseline in \textit{total hours outside of the threshold} for each iteration.
+For instance if in the baseline case \textit{total hours outside of threshold} are 2000 and in an experiment the \textit{total hours outside of threshold} are 1500, we have seen a 25\% decrease.
+
 \subsection*{Simulation}
-For each development period and under each climate change pathway the same eight strategies for carbon mitigation and climate change adaptation to a changing climate were evaluated for their marginal cost of carbon abatement across the whole the Wesbrook development.
+For each development period and under each climate change pathway the same eight strategies for carbon mitigation and climate change adaptation to a changing climate were evaluated for their marginal cost of carbon abatement.
 The simulation procedure for each scenario began with the base-case, under which no strategies were implemented, following with 255 iterations where strategies where implemented alone and in combination with each other.
-This was repeated across both development pathways and both climate change pathways, leading to 1024 iterations of the model.
-The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration.
-At the time of writing radiation analysis was not able to be brought out of a single CPU core and thus steps were taken to minimize the amount of times the command was used as the processing time for the ~120 buildings in the UBEM was 25 minutes.
-In each scenario only 16 experiments required unique radiation profiles.
-These were run first in the loop of 256.
-This is due to some strategies not influencing the radiation simulation output, such as in the \textit{Mass Timber} case.
-The 240 simulations that followed then copied the appropriate output files from the radiation analysis.
-District heating primary energy requirement was modeled post-simulation as the system present in Wesbrook Village is nuanced to its efficiency and fuel source over the day.
-This process is described in the following section on "Operational and embodied carbon".
+This was repeated across both development pathways and both climate change pathways, leading to 1024 total simulations undertaken by the UBEM.
 
@@
 Components and technology costs was gathered through several data sources, \citep{noauthor_cpcn_2014,schlueter_3for2_2016,salasovich_energy_2016,kegel_life_nodate,gordian_rsmeans_2020}.
-The authors recognize that cost is a highly uncertain data point to incorporate into building models.
-While the entire capital and operating cost of each building is not encompassed the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible.
+The authors recognize that cost is a highly uncertain data point to incorporate into building energy models.
+While the entire capital and operating cost of each building do not encompass the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible.
 Cost is assessed as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.
@@
 BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}.
-The district heating provider intends for the system to fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and waste heat fed heat pumps will be created.
+The district heating provider intends for the system tobe  fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and electric heat pumps.
 This system was previously modelled in \citet{mccarty_accepted_2020}.
@@
 
-The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
+The embodied carbon of components and technologies of the models was gathered, similar to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
 The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.
 An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.
-
-\subsection*{Adaptation and mitigation}
-Mitigation was evaluated using the marginal cost of carbon abatement.
-Marginal abatement cost requires two metrics, the first being the net amount of carbon emitted between a base-case and scenario and the net cost between the base-case and scenario.
-In this study the base-case is the first iteration of the 256, where no strategies have been applied.
-Carbon emissions are calculated as the embodied carbon of capital expenditures and the 30-year operating carbon.
-Cost is the 30-year TAC.
-
-Adaptation was considered as the capacity of a building to remain in its comfort threshold while also mitigating carbon emissions.
-The threshold is set to setpoints of the buildings, which are in a majority 21C for heating and 26C for cooling - except where changed by the first strategy.
-The deviation from the threshold is measured as the percent change from the baseline in \textit{total hours outside of the threshold} for each iteration.
-For instance if in the baseline case \textit{total hours outside of threshold} are 2000 and in an experiment the \textit{total hours outside of threshold} are 1500, we have seen a 25\% decrease.
 
@@
 For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic.
-A final open-database is available in the repository mentioned in the abstract.
 From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}.
-These are discussed at more in the following sections but differ in that they are constructed following two logics.
 The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected.
-The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in the first and third frame of Figure \ref{fig:true_macc_both}.
+The latter two are \textit{true} MACCs as described in \ref{fig:true_macc_both}.
 
@@
 Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios.
-Three groups tend to emerge with the most start difference being that one group is emitting far more than the other two.
+Three groups tend to emerge with the most stark difference being that one group is emitting far more than the other two.
 This is a result of those scenarios still relying on the natural-gas based heating system.
-This difference is apparent across both climate change pathways, leading to a conclusion that the impacts of more severe climate are not disrupting mitigation efforts in the model.
+This difference is apparent across both climate change pathways, leading to a conclusion that the impacts of a more severe future climate is not disrupting mitigation efforts as predicted by the model.
 It appears to enable it to an extent.

### 2021-02-01 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 The marginal abatement cost curve (MACC) is an indispensable tool for planning mitigation pathways, but has historically not relied upon robust experimental analysis making it notional at best nor has it included a view of adaptation pathways.
-This study utilizes a newly developed, medium-density residential community in Vancouver, British Columbia, Canada (15,000 residents) as a case study for developing a pathway-based MACC.
+This study utilizes a newly developed, medium-density residential community in Vancouver, British Columbia, Canada as a case study for developing a pathway-based MACC.
 Multiple mitigation and adaptation measures are modeled individually and through exhaustive combination to test their sensitivity on marginal abatement cost and residual cost of climate change.
@@
 This study integrates several climate adaptation strategies into the urban-scale energy simulation process.
-Adaptation strategies are evaluated on the basis of marginal costs of mitigation \textit{and} adaptation, vis-a-vis the influence of individual design strategies on the resilience of the urban development to expectec climate change.
-
+Adaptation strategies are evaluated on the basis of marginal costs of mitigation \textit{and} adaptation, vis-a-vis the influence of individual design strategies on the resilience of the urban development to expected climate change.
 This study will simulate the performance of eight climate mitigation and adaptation strategies alongside one urban development trajectory and two climate change scenarios.
@@
 A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.
-
-The outline of this study is as follows. SecitonXX does..... Seciton XX does....
 
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{}
-%     \caption{The baseline UBEM for Wesbrook Village in BC.}
-%     \label{fig:wesbrook_base}
-% \end{figure}
+\begin{figure*}[hbpt]
+    \centering
+    \includegraphics[scale=0.50]{figures/wesbrook_plan.eps}
+    \caption{The baseline UBEM for Wesbrook Village in BC.}
+    \label{fig:wesbrook_base}
+\end{figure*}
 
@@
     \centering
-    \begin{tabularx}{\textwidth}{|X|X|X|}
+    % \begin{tabularx}{\textwidth}{|X|X|X|}
+    \begin{tabularx}{\linewidth}{|>{\hsize=0.2\hsize}X|
+                              >{\hsize=0.5\hsize}X|
+                              >{\hsize=0.3\hsize}X|}
         \hline
@@
 These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
-defined in \citet{oneill_roads_2017}. Four morphed climate files are produced and described in Figure \ref{fig:weatherfiles}.
+defined in \citet{oneill_roads_2017}. Two morphed climate files were produced at 2050 and 2080 for each pathway.
+
+% and described in Figure \ref{fig:weatherfiles}.
 
@@
 
-Adaptation was considered as the capacity of a building to remain in its comfort threshold while also mitigating carbon emissions.
-The threshold is set to setpoints of the buildings, which are in a majority 21C for heating and 26C for cooling - except where changed by the first strategy.
-The deviation from the threshold is measured as the percent change from the baseline in \textit{total hours outside of the threshold} for each iteration.
-For instance if in the baseline case \textit{total hours outside of threshold} are 2000 and in an experiment the \textit{total hours outside of threshold} are 1500, we have seen a 25\% decrease.
+Adaptation was considered as the capacity of a building to remain within its comfort threshold while also mitigating carbon emissions.
+The threshold considered is between 18\textdegree C and 26\textdegree C.
+For each building in each strategy-set the total amount of hours that interior temperature exceeds the threshold is counted.
+The median value from the buildings is then taken as the adaptation metric for each strategy-set.
 
@@
 Components and technology costs was gathered through several data sources, \citep{noauthor_cpcn_2014,schlueter_3for2_2016,salasovich_energy_2016,kegel_life_nodate,gordian_rsmeans_2020}.
-The authors recognize that cost is a highly uncertain data point to incorporate into building energy models.
-While the entire capital and operating cost of each building do not encompass the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible.
-Cost is assessed as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.
+Cost is a highly uncertain data point to incorporate into building energy models.
+Cost is assessed as the net difference between a strategy-set and the baseline, each calculated as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.
 
@@
 The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps.
-Figure \ref{fig:district_heat_explainer} describes a baseline case of performance with the system.
 Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.
@@
 \section*{Results}
-\begin{figure}[hbpt]
+\begin{figure}[h!]
     \centering
@@
 
-\begin{figure}[hbpt]
+\begin{figure}[h!]
     \centering
@@
 
-Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
-For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier.
+% Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
+For each of the four combinations of development and climate change pathway, %Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier.
 The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%.
@@
 Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions.
-This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}.
+This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}.
+
+% is highlighted in Figure \ref{fig:pareto_plot}.
+
 Figure \ref{fig:true_macc_both} describes how each strategy contributes to the overall decrease in emissions.
@@
 
-\begin{figure}[t]
-    \centering
-    \captionsetup{margin=.5cm}
-    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:pareto_plot}
-\end{figure}
+%\begin{figure}[t]
+%    \centering
+%    \captionsetup{margin=.5cm}
+%    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
+%    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+%    \label{fig:pareto_plot}
+%\end{figure}
 
@@
 \section*{Discussion}
-The use of MACCs, \textit{true} and \textit{illustrative}, offers urban scale energy and development planners a way to compare different types of interventions for their merit as adaptation and mitigation interventions.
-This analysis is robust in that it simulates the technical and financial interaction of the proposed strategies under multiple climate change pathways and following different development trajectories.
-The first limitation lies in the not-so-explicit temporal interaction of the interventions.
+
+\subsection*{Abatement after fuel-switching}
+The context for this study sets up an interesting proposition within BC.
+Electricity in BC is provided primarily via hydroelectricity.
+Emissions within the building sector are therefore driven by natural gas use, either on-site or within district systems.
+The two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition, the use of natural gas must be eliminated.
+This however raises the point of how abatement should continue once the significant reductions are made and systems are then relying on a near-carbon-free grid.
+At present, BC (and UBC) expects new buildings to be net-zero \textit{energy} ready by the early 2030s, with no clear objectives on whether buildings should be truly net-zero energy (NZE) in a more distant future.
+There is reason for this, as evidenced by the modelling undertaken in this work.
+This study showed that in testing rooftop PV systems for medium density developments, PV systems will not yield large emissions reductions under any scenario.
+In the worst-case climate scenario rooftop panels alone reduced emissions by only 4.4\%.
+
+%Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}.
+This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.
+
+\subsection*{Limitations of approach}
+
+The first limitation of this study lies in the not-so-explicit temporal interaction of the interventions.
 Each building was modeled as having its own unique construction and retrofit dates, which contribute to the emissions and total annualized cost profile for each run of the district energy model.
@@
 
-\subsection*{Strategy choice}
 A major limitation in the framework underpinning this study is the finite space of strategy choice.
 We test eight strategies here that are applied generally across the district.
-This may not always be a problem if prior to the study a strategy evaluation study is conducted or subject-matter experts are brought in to help establish priors.
+This may not always be a problem if prior to the study a strategy evaluation is conducted or subject-matter experts are brought in to help establish priors.
 Future efforts need to be more precise with strategy implementation based on building or site need.
-
-\subsection*{Abatement after fuel-switching}
-The context for this study sets up an interesting proposition within BC.
-The electrical grid is majority hydroelectric.
-Emissions within the building sector are therefore driven by natural gas use, either on site or within district systems.
-The two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition the use of natural gas must be eliminated.
-This however raises the point of how abatement should continua once the significant reductions are made and systems are then relying on a near-carbon free grid.
-Future building code intends for new buildings to be net-zero \textit{energy} ready, but this study showed in testing rooftop photovoltaic that for this type of density, just rooftop panels are not going to generate significant amounts of energy or contribute to emissions reductions; in the worst-case climate scenario rooftop panels alone reduced emissions by 4.4\%.
-
-Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}.
-This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.
 
@@
 \section*{Conclusion}
-In this study the output of 1024 different urban building energy simulations was discussed in the context of use marginal abatement cost curves and complimentary visualizations to make decisions regarding mitigation and adaptation planning for a medium-density community in Vancouver, British Columbia.
-The simulations were differing combinations of development completeness of the community, climate change pathway (between best- and worst-case scenarios), and eight mitigation and adaptation strategies.
+In this study the output of 1024 different urban building energy simulations was used to generate marginal abatement cost curves and complimentary visualizations to make decisions on climate mitigation and adaptation at an urban scale.
+A case study of Wesbrook Village, a planend 25,000-member residential community in Vancouver, Canada was used.
 
 The resulting MACCs were created from two perspectives.
-First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) provide general guidance on choosing sets of strategies to achieve mitigation under different planning constraints.
-The \textit{true} MACCs (Figure \ref{fig:true_macc_both}) reveal how the individual strategies within a set interact to technically and financially to ultimately abate a certain amount of carbon.
-The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria using a plot of pareto optimums (Figure \ref{fig:pareto_plot}).
-This enables planners to begin to assess adaptation targets alongside abatement.
+First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) sought to provide general guidance on which strategies achieve targeted mitigation under different planning constraints.
+The \textit{true} MACCs (Figure \ref{fig:true_macc_both}) reveal how the individual strategies within a set interact technically and financially to ultimately abate a certain amount of carbon.
+The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria.
+
+% using a plot of pareto optimums (Figure \ref{fig:pareto_plot}). This enables planners to begin to assess adaptation targets alongside abatement.
 

### 2021-02-01 manuscript_wesbrook-bigmacc_BS2021.tex

@@
 
+\begin{figure*}[hbpt]
+    \centering
+    \includegraphics[scale=0.50]{figures/wesbrook_plan.eps}
+    \caption{The baseline UBEM for Wesbrook Village in BC.}
+    \label{fig:wesbrook_base}
+\end{figure*}
+
 In the presence of limited resources and a range of objectives, the cost and benefit of proposed strategies need to be assessed on their own and while interacting with other strategies, as well as under the uncertainty of climate change and human action.
@@
 
-\begin{figure*}[hbpt]
-    \centering
-    \includegraphics[scale=0.50]{figures/wesbrook_plan.eps}
-    \caption{The baseline UBEM for Wesbrook Village in BC.}
-    \label{fig:wesbrook_base}
-\end{figure*}
-
 \subsection*{Wesbrook Village} 
@@
 With its current building codes, UBC does intend that space cooling may be a required energy service in the community in the next decade \citep{noauthor_residential_2021}.
+
+\begin{table*}[ht]
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+    \caption{Each strategy as it was applied in the simulations.}
+    \footnotesize
+    \label{tab:strategies}
+    \centering
+    % \begin{tabularx}{\textwidth}{|X|X|X|}
+    \begin{tabularx}{\linewidth}{|>{\hsize=0.2\hsize}X|
+                              >{\hsize=0.5\hsize}X|
+                              >{\hsize=0.3\hsize}X|}
+        \hline
+        \bf{Strategy} & \bf{Description} & \bf{Scale} \\
+        \hline
+        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings \\
+        \hline
+        Green Roof & Install green roofs for insulative, albedo, and heat gain benefits. & All Buildings \\
+        \hline
+        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings \\
+        \hline
+        Passive House & Require passive house building codes for envelope. & New Buildings \\
+        \hline
+        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings \\
+        \hline
+        Mass Timber & Construction must utilize mass timber. & New Buildings \\
+        \hline
+        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings \\
+        \hline
+        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings \\
+        \hline
+    \end{tabularx}
+    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
+\end{table*}
 
@@
 
-\begin{table*}[ht]
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-    \caption{Each strategy as it was applied in the simulations.}
-    \footnotesize
-    \label{tab:strategies}
-    \centering
-    % \begin{tabularx}{\textwidth}{|X|X|X|}
-    \begin{tabularx}{\linewidth}{|>{\hsize=0.2\hsize}X|
-                              >{\hsize=0.5\hsize}X|
-                              >{\hsize=0.3\hsize}X|}
-        \hline
-        \bf{Strategy} & \bf{Description} & \bf{Scale} \\
-        \hline
-        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings \\
-        \hline
-        Green Roof & Install green roofs for insulative, albedo, and heat gain benefits. & All Buildings \\
-        \hline
-        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings \\
-        \hline
-        Passive House & Require passive house building codes for envelope. & New Buildings \\
-        \hline
-        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings \\
-        \hline
-        Mass Timber & Construction must utilize mass timber. & New Buildings \\
-        \hline
-        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings \\
-        \hline
-        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings \\
-        \hline
-    \end{tabularx}
-    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-\end{table*}
-
 \subsection*{Urban Building Energy Model (UBEM)}
@@
 
-\subsection*{Operational and embodied carbon}
-Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service.
-BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}.
-The district heating provider intends for the system tobe  fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and electric heat pumps.
-This system was previously modelled in \citet{mccarty_accepted_2020}.
-Its carbon intensity was estimated to be between an annual average of 10.8 and 180.0 kgCO2e/kWh.
-The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps.
-Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.
-
-The embodied carbon of components and technologies of the models was gathered, similar to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
-The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.
-An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.
-
-%---------------------------------------------------------------------------------------
-\section*{Results}
-\begin{figure}[h!]
+\begin{figure}[t!]
     \centering
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
     \centering
@@
 
+\subsection*{Operational and embodied carbon}
+Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service.
+BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}.
+The district heating provider intends for the system tobe  fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and electric heat pumps.
+This system was previously modelled in \citet{mccarty_accepted_2020}.
+Its carbon intensity was estimated to be between an annual average of 10.8 and 180.0 kgCO2e/kWh.
+The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps.
+Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.
+
+The embodied carbon of components and technologies of the models was gathered, similar to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
+The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.
+An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.
+
+%---------------------------------------------------------------------------------------
+\section*{Results}
+
 The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building.
@@
 The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected.
-The latter two are \textit{true} MACCs as described in \ref{fig:true_macc_both}.
+The latter two are \textit{true} MACCs as described in Figure \ref{fig:true_macc_both}.
 
@@
 
-% Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario.
-For each of the four combinations of development and climate change pathway, %Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier.
-The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%.
-The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented.
-These charts can inform the creation of a \textit{true} MACC by informing which strategy set is chosen based on not only marginal abatement cost, but also the adaptation metric.
+\begin{figure}[t!]
+    \centering
+    \captionsetup{margin=.5cm}
+    \includegraphics[scale=0.45]{figures/pareto_plots_585_box_update.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:pareto_plot}
+\end{figure}
 
 Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions.
-This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}.
-
-% is highlighted in Figure \ref{fig:pareto_plot}.
+This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}, highlighted in Figure \ref{fig:pareto_plot}.
+Marginal abatement cost and the adaptation metric were plotted in Figure \ref{fig:pareto_plot} to evaluate optimal fronts of each scenario.
 
@@
 % \end{figure*}
-
-%\begin{figure}[t]
-%    \centering
-%    \captionsetup{margin=.5cm}
-%    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
-%    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-%    \label{fig:pareto_plot}
-%\end{figure}
 

### 2021-04-13 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

@@
 \usepackage{tabularx}
+\usepackage{draftwatermark}
+\SetWatermarkText{DRAFT}
+\SetWatermarkScale{5}
 %-----------------------------SET SKIP SPACES -------------------------------------------------------------------
@@
 \author{																																														% Line 3
-% Justin McCarty$^1$, Adam Rysanek$^1$
+Justin McCarty$^1$, Adam Rysanek$^1$
 \\ 																				% Line 4
@@
 A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.
+
+% Following this a brief introduction to the context of the study, Wesbrook Village is presented and then formats for visualizing mitigation and adaptation data are introduced.
+After these introductions, the Methods section presents the urban building energy model, mitigation and adaptation strategies, simulation format, and lastly the costing and carbon accounting methodology and data sources.
+The Results are then presented first as general performance of the strategies and then utilizing the visualization formats introduced in earlier several figures are drawn in the context of theoretical mitigation and adaptation planning for the development.
+The results and methods are then discussed for their limitations and impacts on climate change planning efforts in the community.
 
@@
 Another \textit{illustrative} MACC was drawn, seen in Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
-All bars represet strategy-sets that would reach that reductions total, ultimately \textit{0111000} is chosen at the marginal abatement cost of -\$50.
+All bars represent strategy-sets that would reach that reductions total, ultimately \textit{0111000} is chosen at the marginal abatement cost of -\$50.
 

### 2021-04-14 second_submissions.tex
Revisions

--- 2021-04-13 manuscript_wesbrook-bigmacc_BS2021.tex
@@
 \usepackage{tabularx}
-\usepackage{draftwatermark}
-\SetWatermarkText{DRAFT}
-\SetWatermarkScale{5}
 %-----------------------------SET SKIP SPACES -------------------------------------------------------------------
@@
 \author{																																														% Line 3
-Justin McCarty$^1$, Adam Rysanek$^1$
+% Justin McCarty$^1$, Adam Rysanek$^1$
 \\ 																				% Line 4
@@
 
-\begin{figure*}[hbpt]
+\begin{figure}[hbpt]
     \centering
-    \includegraphics[scale=0.50]{figures/wesbrook_plan.eps}
+    \includegraphics[scale=0.28]{figures/wesbrook_plan.eps}
     \caption{The baseline UBEM for Wesbrook Village in BC.}
     \label{fig:wesbrook_base}
-\end{figure*}
+\end{figure}
 
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[scale=1.5]{figures/sample_sequence.eps}
-%     \caption{Each scenario iterated through 256 combinations of strategy implementation.}
-%     \label{fig:sample_sequence}
-% \end{figure}
+\subsection*{Wesbrook Village}
 
-\subsection*{Wesbrook Village} 
-% Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
 Wesbrook Village is a new residential community under construction by the University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}.
-On it completion within the next decade, the community will provide permanent housing for over 25,000 residents of Vancouver, BC primarily in mid-rise (4-6 stories) and high-rise residential towers (15-30 stories).
+On its completion within the next decade, the community will provide permanent housing for over 25,000 residents of Vancouver, BC primarily in mid-rise (4-6 stories) and high-rise residential towers (15-30 stories).
 
@@
 Buildings of the Wesbrook community make use of mix of energy systems.
-Some buildings provide space heating using hydronic in-floor radiant systems; some provide space heating via electric baseboard heaters.
+Some buildings provide space heating through hydronic in-floor radiant systems; some through electric baseboard heaters.
 Some buildings operate dedicated boilers for generating hot water; other buildings receive hot water from a natural gas-fired district energy system.
@@
     \begin{tabularx}{\linewidth}{|>{\hsize=0.2\hsize}X|
-                              >{\hsize=0.5\hsize}X|
-                              >{\hsize=0.3\hsize}X|}
+                              >{\hsize=0.4\hsize}X|
+                              >{\hsize=0.15\hsize}X|
+                              >{\hsize=0.25\hsize}X|}
         \hline
-        \bf{Strategy} & \bf{Description} & \bf{Scale} \\
+        \bf{Strategy} & \bf{Description} & \bf{Scale} & \bf{Embodied CO\textsubscript{e} Source} \\
         \hline
-        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings \\
+        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings & N/A \\
         \hline
-        Green Roof & Install green roofs for insulative, albedo, and heat gain benefits. & All Buildings \\
+        Green Roof & Install green roofs for insulation, albedo, and heat gain benefits. & All Buildings & \citep{jones_ice_2019}\\
         \hline
-        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings \\
+        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings & \citep{jones_ice_2019, rodriguez_embodied_2019} \\
         \hline
-        Passive House & Require passive house building codes for envelope. & New Buildings \\
+        Passive House & Require passive house building codes for envelope. & New Buildings & \citep{jones_ice_2019} \\
         \hline
-        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings \\
+        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings & \citep{rodriguez_embodied_2019} \\
         \hline
-        Mass Timber & Construction must utilize mass timber. & New Buildings \\
+        Mass Timber & Construction must utilize mass timber. & New Buildings & \citep{c-change_labs_embodied_2020} \\
         \hline
-        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings \\
+        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings & \citep{noauthor_cpcn_2014, jones_ice_2019} \\
         \hline
-        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings \\
+        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings  & \citep{jones_ice_2019} \\
         \hline
@@
 New buildings are however built to a performance profile modeled after expected changes in the community's building performance code (\citep{noauthor_residential_2021}).
-
-% \begin{table*}[h]
-%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-%     \caption{The first two-column table.}
-%     \label{tab:code_trajectory}
-%     \centering
-%     \begin{tabular}{ | c | c | c | }
-%         \hline
-%         \bf{Year} & \bf{Code Name} 2 & \bf{Performance Note} \\
-%         \hline
-%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
-%         \hline
-%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
-%         \hline
-%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
-%         \hline
-%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
-%         \hline
-%     \end{tabular}
-%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
-% \end{table*}
 
@@
 The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{cwec_2016} was morphed, following the algorithms set out by \citet{belcher_constructing_2005} and expanded upon by \citet{jentsch_climate_2008}.
+A 25-member ensemble of climate model output data from Climate Model Intercomparison Project 6 (CMIP6) models was used in the morphing process.
 Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios.
@@
 defined in \citet{oneill_roads_2017}. Two morphed climate files were produced at 2050 and 2080 for each pathway.
-
-% and described in Figure \ref{fig:weatherfiles}.
 
@@
 
-A single entire simulation process (1024 iterations) required 64 hours of processing, utilizing 14 threads from an Intel i9-9900 8-core CPU at 4.6GHz, requiring 20GB of free RAM and an end storage requirement over 2TB of uncompressed results files.
+% A single entire simulation process (1024 iterations) required 64 hours of processing, utilizing 14 threads from an Intel i9-9900 8-core CPU at 4.6GHz, requiring 20GB of free RAM and an end storage requirement over 2TB of uncompressed results files.
 This detail is mentioned to help readers understand the scale of computing required to undertake simulations of this scale and to seek methods and functions that optimize processing times.
@@
 Cost is a highly uncertain data point to incorporate into building energy models.
-Cost is assessed as the net difference between a strategy-set and the baseline, each calculated as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.
+Cost is assessed as the net difference between a strategy-set and the baseline, each calculated as the 30-year total annualized cost (TAC), shown in Eq.
+1, from within the City Energy Analyst, applying a 5\% discount rate, which was chosen after consulting the local developers and planners.
 
-\begin{figure}[t!]
+\begin{equation}
+C_{ann,tot} = CRF(i,R)C_{NPC,tot}
+\end{equation}
+
+Total Annualized Cost is the annualized value of the total net present cost where \textit{CRF} is the Cost Recovery Factor, requiring \textit{i}, the annual real discount rate, and \textit{R}, the lifetime considered.
+C\textsubscript{NPC,tot} is the total net present cost for the lifetime considered.
+
+\begin{figure}[t]
     \centering
@@
 
-\begin{figure}[t!]
+\begin{figure}[t]
     \centering
     \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
-    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios.
-The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
+    \caption{Here we compare the demand on the district heating system and show, in the highlighted gap, where less natural gas was used due to the generally warmer winter in SSP585.}
     \label{fig:compare_district}
@@
 BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}.
-The district heating provider intends for the system tobe  fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and electric heat pumps.
+The district heating provider intends for the system to be fed entirely from natural gas boilers until 2023 at which point there will be a transition to a more complex system of natural gas peaking boilers and wate-heat primed electric heat pumps.
 This system was previously modelled in \citet{mccarty_accepted_2020}.
@@
 
-The embodied carbon of components and technologies of the models was gathered, similar to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon.
+The embodied carbon of components and technologies of the models was gathered, similar to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate.
 The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved.
@@
 \section*{Results}
-
 The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building.
@@
 The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected.
-The latter two are \textit{true} MACCs as described in Figure \ref{fig:true_macc_both}.
+The latter two are \textit{true} MACCs as described in \ref{fig:true_macc_both}.
 
@@
     \includegraphics[scale=0.95]{figures/true_maccs_waterfalls_both.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \caption{Here two sets of plots are shown for two strategy sets.
+The top of each set shows the contribution of each strategy to the the strategy set's overall carbon emissions reduction.
+The bottom shows the MAC breakdown within each strategy set.}
     \label{fig:true_macc_both}
@@
 
-\begin{figure}[t!]
-    \centering
-    \captionsetup{margin=.5cm}
-    \includegraphics[scale=0.45]{figures/pareto_plots_585_box_update.eps}
-    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-    \label{fig:pareto_plot}
-\end{figure}
-
 Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions.
-This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}, highlighted in Figure \ref{fig:pareto_plot}.
+This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}.
 Marginal abatement cost and the adaptation metric were plotted in Figure \ref{fig:pareto_plot} to evaluate optimal fronts of each scenario.
@@
 
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
-%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-%     \label{fig:MACC_true_noDH}
-% \end{figure}
-
-A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario.
+A second \textit{true} MACC was generated under the plan to abate as much carbon as possible while continuing to use the district heating system, under the worst-case climate scenario.
 Figure \ref{fig:true_macc_both} describes how each measure contributes to overall emissions reduction.
@@
 
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
-%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-%     \label{fig:MACC_true_DH}
-% \end{figure}
-
-% \begin{figure*}[hbpt]
-%     \centering
-%     \includegraphics[scale=0.8]{figures/optimal_plots.eps}
-%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
-%     \label{fig:pareto_plot}
-% \end{figure*}
-
+\begin{figure}[t!]
+    \centering
+    \captionsetup{margin=.5cm}
+    \includegraphics[scale=0.40]{figures/pareto_plots_585_box_update.eps}
+    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
+    \label{fig:pareto_plot}
+\end{figure}
 %---------------------------------------------------------------------------------------
@@
 The context for this study sets up an interesting proposition within BC.
-Electricity in BC is provided primarily via hydroelectricity.
+Electricity in BC is provided primarily via hydroelectricity; the electrical gird is considered 98\% clean energy \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}.
 Emissions within the building sector are therefore driven by natural gas use, either on-site or within district systems.
@@
 
-%Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}.
+Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}.
 This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.
+An increase in emissions is seen with the implementation of a seawater cooling loop, likely due to the fact that conventional methods of space cooling rely on a near-zero carbon grid to begin with and are not as intense from an embodied carbon perspective.
 
@@
 
+In creating the morphed weather files, we used climate model data from global climate models and not regional climate models.
+This is typical practice for morphing, particularly if you want to adjust weather variables beyond temperature.
+However it is a limitation particularly in a region such as Southwestern, BC that is highly mountainous and coastal.
+Future efforts for morphing should address these limitations with climate model data that is either regionally generated or downscaled.
+
+The increase in cost of energy services was not accounted for dynamically.
+It would be expected, particularly in a country with a progressive carbon tax, that the cost of natural gas and electricity will increase over the coming decades, and outpace inflation-related increases.
+Future analysis must take this into account, as well as seek to differ the increase across climate change scenarios, which have different economic assumptions underpinning their respective increases in greenhouse gas emissions.
 %---------------------------------------------------------------------------------------
@@
 In this study the output of 1024 different urban building energy simulations was used to generate marginal abatement cost curves and complimentary visualizations to make decisions on climate mitigation and adaptation at an urban scale.
-A case study of Wesbrook Village, a planend 25,000-member residential community in Vancouver, Canada was used.
+A case study of Wesbrook Village, a planned 25,000-member residential community in Vancouver, Canada was used.
 
@@
 
-% using a plot of pareto optimums (Figure \ref{fig:pareto_plot}). This enables planners to begin to assess adaptation targets alongside abatement.
-
 The analysis had limitations discussed in the literature on using MACCs for decision-support.
 These include being more realistic about building technology and component lifetimes, which requires the framework to consider retirement.
-As well the study is constrained by computational resources and known mitigation and adaptation strategies for the site.
+As well the study is constrained by computational resources (each 1024 iteration took 64 hours) and known mitigation and adaptation strategies for the site.
 Future studies should seek to better understand either through exploratory analysis or expert elicitation, which strategies are reasonable for the market and context.
@@
 \section*{Acknowledgment}
+This project was funded by the Pacific Institute for Climate Solutions (PICS) Energy Efficiency in the Built Environment Project (grant number PICS 36170-50280).
 

### 2021-06-08 bigmacc_bs2021_revised_manuscript_clean.tex
Updates from Overleaf

--- 2021-04-14 second_submissions.tex
@@
 \renewcommand\refname{References}
+
 %END OF THE SETUP
@@
 \title{%
-Simulation and visualization framework for selecting appropriate urban-scale climate mitigation and adaptation strategies} 																																% Line 2 
+Simulation and visualization framework for selecting appropriate urban-scale % Line 1
+climate mitigation and adaptation strategies} % Line 2 
 %If there is no second line then just put \phantom{Line 2} here
@@
 %%% Do not exceed more than 6 lines for authors and affiliations
-\author{																																														% Line 3
-% Justin McCarty$^1$, Adam Rysanek$^1$
-\\ 																				% Line 4
-% $^1$The University of British Columbia, Vancouver, Canada
-\\ 																																                                                            	% Line 5
-% $^2$Institution 2, City 2, Country 2
-\\ 																																                                                                % Line 6
+\author{%
+Justin McCarty$^1$, Adam Rysanek$^1$ % Line 4
+\\ 	
+$^1$School of Architecture and Landscape Architecture, \\ % Line 5
+The University of British Columbia, Vancouver, BC, Canada % Line 6
 % comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
 % \textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}
+% \textit{(leave blank up to line 10 - remove line numbering from final version)}
+
 \\ % Line 7 																				
-% \textit{(leave blank up to line 10 - remove line numbering from final version)}
 \\ % Line 8																			
-\phantom{Line 9}} 																																								            	% Line 9
+\phantom{Line 10}} 																																								            	% Line 9
 \date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														                                                            % Line 10
